---
title: "figures"
output: html_document
---

Manuscript ID: RSTB-2025-0484

Title: Water availability affects West Nile virus dynamics in a heavily managed agricultural landscape

Authors: Samantha Sambado, Andrew J. MacDonald, Alex Konings, and Erin A. Mordecai

Corresponding author: ssambado@stanford.edu

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(sf)
library(tigris)
library(ggpubr)
library(patchwork)
library(ggspatial)
library(devtools)
#devtools::install_github("an-bui/calecopal")
library(calecopal)
names(cal_palettes)
library(paletteer)
library(broom)
library(here)
library(maps)
library(wesanderson)

## upload station data

## upload ca shapefile
options(tigris_use_cache = TRUE)
ca <- tigris::counties("ca", class = "sf", cb = TRUE, resolution = "20m")

## upload cv
cv <- st_read(here("data", "spatial_boundaries", "centralvalley", "centralvalley.shp"))

## theme style
theme_style <- theme(legend.title = element_text(size = 14, face = "bold"),
                     legend.text = element_text(size = 13),
                     plot.margin = margin(0,0,0,0)) +
  theme_void()


```


# Main Text

## Figure 1

### Part A - Precip (Where)
format data
```{r}
### upload
#prism_annual <- terra::rast(here("data", "raw", "public", "prism_ppt_us_30s_2020_avg_30y", #"prism_ppt_us_30s_2020_avg_30y.tif"))
#
### correct crs
#ca_prism <- st_transform(ca, crs = crs(prism_annual))
#prism_crop <- crop(prism_annual, ca_prism)
#prism_mask <- mask(prism_crop, ca_prism)
#
### turn into dataframe
#prism_df <- as.data.frame(prism_mask, xy = TRUE)
#names(prism_df)[3] <- "precip"
#
### align alluvial boundary
#cv_prism <- st_read(here("data", "spatial_boundaries", "centralvalley", "centralvalley.shp")) %>% 
#  st_transform(st_crs(ca_prism))
```

plot data
```{r}
#fig_1_a <- ggplot() +
#  geom_raster(data = prism_df, aes(x = x, y = y, fill = precip)) +
#  geom_sf(data = cv_prism, fill = NA, color = "black", size = 0.6) +
#  coord_sf(expand = FALSE) +
#  theme_style +
#  scale_fill_gradientn(colors = cal_palette("sbchannel", type = "continuous", n = 15),
#                       breaks = c(1000,4000), limits = c(0, 4000),
#                       guide = guide_colorbar(title.hjust = 0.5)) +
#  labs(fill = "Precip. (mm)") +
#  theme(legend.position = c(0.715, 0.73),
#        legend.key.width = unit(0.6, "cm"),
#        legend.key.height = unit(0.4, "cm"),
#        legend.title = element_text(face = "bold", size = 14)) +
#  annotate("text", x = -119.2, y = 41.5, label = "A", fontface = "bold", size = 10) +
#  annotation_scale(location = "bl", width_hint = 0.22, pad_x = unit(.2, "cm"), pad_y = unit(.2, "cm")) #+
#  annotation_north_arrow(location = "bl",  pad_x = unit(.2, "cm"), pad_y = unit(1.2, "cm"))
#
#ggsave(fig_1_a, file = here("outputs", "figures", "main", "fig_1_a_v1.png"), dpi = 400, bg = "white")
```

### Part B - Precip (When)
format data
```{r}
#### wrangle data 
# need to make loop to call in
prism_tif_files <- list.files(here("data", "raw", "public", "prism_normals_precip_800m_monthly"), 
                              pattern = "\\.tif$", full.names = TRUE, recursive = TRUE)
prism_tif_files <- sort(prism_tif_files) # make sure its 01-12
prism_monthly <- terra::rast(prism_tif_files)

# make month name from file name
month_nums <- str_extract(prism_tif_files, "(?<=_)\\d{6}(?=_)") #this gives yearmonth 
month_nums <- substr(month_nums, 5,6) # this extracts month
names(prism_monthly) <- paste0("X", as.numeric(month_nums)) # change column names

## align crs, crop, mask
ca_prism_vect <- vect(st_transform(ca, crs(prism_monthly)))
prism_monthly_crop <- crop(prism_monthly,ca_prism_vect)
prism_monthly_mask <- mask(prism_monthly_crop, ca_prism_vect)

## align hydro region (HR)
HR_prism <- st_read(here("data", "spatial_boundaries", "i03_Hydrologic_Regions", "i03_Hydrologic_Regions.shp")) %>%
  st_transform(st_crs(prism_monthly_mask))

HR_prism_vect <- vect(HR_prism)

## extract precip per HR
HR_prism_monthly <- terra::extract(prism_monthly_mask, HR_prism_vect, fun = mean, na.rm = TRUE)

## make tidy format
HR_prism_monthly_df <- HR_prism_monthly %>% 
  mutate(region = HR_prism_vect$HR_NAME) %>% 
  group_by(region) %>% 
  summarise(across(starts_with("X"), mean, na.rm = TRUE)) %>% 
  pivot_longer(cols = starts_with("X"), names_to = "month", values_to = "precip") %>% 
  mutate(month = factor(as.numeric(gsub("X", "", month)), levels = 1:12, labels = month.abb))
```

plot data
```{r}

#fig_1_b <- HR_prism_monthly_df %>% 
#  filter(region == "Sacramento River" | region == "San Joaquin River" | region == "Tulare Lake") %>% 
#  ggplot(aes(x = month, y = precip, color = region, group = region)) +
#  geom_line(size = 1.5) +
#  geom_point(size = 4) +
#  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005")) +
#  labs(y = "Precip. (mm)", color = "Hydrologic Region", x = NULL) +
#  theme_bw() +
#  theme(legend.position =c(0.55,.59), 
#        axis.title = element_text(size = 15, face = "bold"),
#        axis.text.x = element_text(size = 14),
#        axis.text.y = element_text(size = 14),
#        panel.grid = element_blank(),
#        legend.title = element_text(size = 17, face = "bold"),
#        legend.text  = element_text(size = 16),
#        plot.margin = margin(0,0,0,0))   +
#  scale_x_discrete(expand = c(0.02,0)) +
#  scale_y_continuous(expand = c(0.02,0)) +
#  annotate("text", x = 1.8, y = 170, label = "B", fontface = "bold", size = 10)

#ggsave(fig_1_b, file = here("outputs", "figures", "main", "fig_1_b_v1.png"), dpi = 400, bg = "white")
```

save top figure for presentations
```{r}
#fig_1_top <- fig_1_a + fig_1_b
#ggsave(fig_1_top , file = here("outputs", "figures", "main", "fig_1_top_v1.png"), dpi = 400, bg = #"white", width = 12)
```

### Part C - Water features
format data
```{r}
## get everything in the correct crs
target_crs <- 3310
cv_3310 <- st_transform(cv, target_crs)

## rivers 
rivers_major <- st_read(here("data","raw", "public", "NHD_Major_Rivers","NHD_Major_Rivers.shp" )) %>% 
  st_zm(drop = TRUE) %>% 
  st_transform(target_crs)

# only select rivers within central valley
rivers_major_cv <- st_intersection(rivers_major, cv_3310) 

## wetlands
wetlands <- st_read(here("data","raw", "public", "wetlands_cv.gpkg"), layer = "CA_Wetlands") %>%
  st_transform(target_crs)

## hr regions
HR_cv <- st_read(here("data", "spatial_boundaries", "i03_Hydrologic_Regions", "i03_Hydrologic_Regions.shp")) %>% 
  st_transform(st_crs(cv_3310))
  
# only plot
HR_cv_clip <- st_intersection(HR_cv, cv_3310)

```

plot data
```{r}
# set basin colors
HR_colors <- ifelse(HR_cv_clip$HR_NAME == "Sacramento River", alpha("#ADC397", 0.4),
                    ifelse(HR_cv_clip$HR_NAME == "San Joaquin River", alpha("#DFBF2B", 0.4),
                           ifelse(HR_cv_clip$HR_NAME == "Tulare Lake", alpha("#EA8005", 0.4),
                                  "#f0f0f0")))


fig_1_c <- ggplot() +
  geom_sf(data = ca, fill = "grey97", color = NA, size = 0.3) +
    geom_sf(data = cv_3310, fill = "white", color = "black", size = 0.6) +
  geom_sf(data = HR_cv_clip, fill = HR_colors, color = NA) +
  # add water features
  geom_sf(data = rivers_major_cv, aes(linetype = "Rivers"), color = "#1D91C0", linewidth = 0.8) +
  geom_sf(data = wetlands, aes(fill = "Wetlands"), color = NA) +
  # make manual legend
  scale_fill_manual(name = "Water Features", values = c("Wetlands" = "#2CA25F")) +
  scale_linetype_manual(name = "", values = c("Rivers" = 1)) +
  guides(linetype = guide_legend(override.aes = list(linewidth = 4)))+
  theme_style +
  theme(legend.text = element_text(size = 15),
        legend.title = element_text(size = 14, face = "bold"),
        legend.position =c(0.86,.87))  +
  coord_sf(xlim = c(-122.7, -118.4), ylim = c(34.7, 40.4), crs = 4326, expand = FALSE)  +
  annotate("text", x = -120.5, y = 40.1, label = "B", fontface = "bold", size = 10) +
  annotate("text", x = -120.8, y = 39.4, label = "Sac.\nRiver\nHR", size = 8) +
  annotate("text", x = -119.8, y = 38, label = "San\nJoaquin\nRiver\nHR", size = 8) +
  annotate("text", x = -121.0, y = 36, label = "Tulare\nLake\nHR", size = 8) +
  annotation_scale(location = "bl", width_hint = 0.22, pad_x = unit(.2, "cm"), pad_y = unit(.2, "cm")) +
  annotation_north_arrow(location = "bl",  pad_x = unit(.2, "cm"), pad_y = unit(1.2, "cm"))

ggsave(fig_1_c, file = here("outputs", "figures", "main", "fig_1_c_v2.png"), dpi = 400, bg = "white")
```


### Part D - Irrigation type
format data
```{r}
### get everything in the correct crs
target_crs <- 3310
cv_3310 <- st_transform(cv, target_crs)
#
#iq <- st_read(here("data", "raw", "public", "i15_crop_mapping_2022_shp", "i15_crop_mapping_2022.shp")) #%>% 
#  st_zm(drop = TRUE) %>% 
#  st_transform(target_crs)
#
### some messy boarders so try simplifying
#iq_valid <- st_make_valid(iq) 
#iq_valid <- iq_valid[!st_is_empty(iq_valid),] # remove empty geoms
#
## clip to only central valley
#iq_cv <- st_intersection(iq_valid, cv_3310)
#
### save to pull this up later for heat extreme proj
##saveRDS(iq_cv, "landIQ_cv_2022.rds")

iq_cv <- readRDS(here("data", "interim", "landIQ_cv_2022.rds"))

### pull out crop data to filter on later
## these are 2-3 digit codes but the first letter is the main crop type - this could be refined
iq_cv <- iq_cv %>% 
  mutate(main_letter = substr(MAIN_CROP, 1, 1))

unique(iq_cv$main_letter)

## assign irrigation type 
irrigation_type <- data.frame(crop_group = c("F", "I", "P", "G" ,"T", "Y", "X", "D", "C", "V", "R", "*")) %>% 
  mutate(irrigation = case_when(crop_group %in% c("R",  "P") ~ "Flood",
                                crop_group %in% c("G","F") ~ "Sprinkler",
                                crop_group %in% c("V", "C", "D", "T", "Y") ~ "Drip",
                                TRUE ~ "Unknown"))
iq_cv_irrigation <- iq_cv %>% 
  left_join(irrigation_type, by = c("main_letter" = "crop_group")) %>% 
  mutate(irrigation = case_when(is.na(irrigation) ~ "Urban",
                                TRUE ~ irrigation)) %>% 
  mutate(irrigation = factor(irrigation, 
                             levels = c("Flood", "Sprinkler", "Drip", "Unknown", "Urban")))

```

plot data
```{r}
## make hydro colors
irrigation_colors <- c("Flood" = "#e31a1c",
                       "Sprinkler" = "#6592d6",
                       "Drip" = "#cce5ff",
                       "Urban" = "#d9d9d9")

fig_1_d <- ggplot() +
  geom_sf(data = ca, fill = "grey97", color = NA, size = 0.3) +
  geom_sf(data = cv_3310, fill = "white", color = "black", size = 0.6) +
  geom_sf(data = iq_cv_irrigation, aes(fill = irrigation), color = NA) +
  scale_fill_manual(values = irrigation_colors, na.value = "#f0f0f0") +
  labs(fill = "Irrigation Type") +
  theme_style +
  theme(legend.text = element_text(size = 15),
        legend.title = element_text(size = 14, face = "bold"),
        legend.position =c(0.86,.87)) +
  coord_sf(xlim = c(-122.7, -118.4), ylim = c(34.7, 40.4), crs = 4326, expand = FALSE) +
  annotate("text", x = -120.5, y = 40.1, label = "C", fontface = "bold", size = 10)


ggsave(fig_1_d, file = here("outputs", "figures", "main", "fig_1_d_v2.png"), dpi = 400, bg = "white")
```

**Combine for full Fig 1**
```{r}
## split into top/bottom rows
#bottom_row <- (fig_1_c | plot_spacer() | fig_1_d) +
#  plot_layout(widths = c(1, 0.04, 1))  # tiny gap
#
#top_row <- fig_1_a | fig_1_b
#
#fig_1_full <- top_row / bottom_row +
#  plot_layout(heights = c(0.8, 2))
#
#ggsave(fig_1_full, file = here("outputs", "figures", "main", "fig_1_full_v1.png"), 
#       dpi = 400, bg = "white",
#       width = 12, height = 12)


```

new Fig 1 based on Erin's and Alex's suggestions

```{r}
## precip
fig_1_a_pp <- HR_prism_monthly_df %>% 
  filter(region == "Sacramento River" | region == "San Joaquin River" | region == "Tulare Lake") %>% 
  mutate(month = match(month, month.abb)) %>% 
  ggplot(aes(x = month, y = precip, color = region, group = region)) +
  geom_line(size = 1.5) +
  geom_point(size = 4) +
  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005")) +
  labs(y = "Precip. (mm)", color = "Hydrologic Region", x = NULL) +
  theme_bw() +
  theme(legend.position =c(0.58,.70), 
        axis.title = element_text(size = 15, face = "bold"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        panel.grid = element_blank(),
        legend.title = element_text(size = 15, face = "bold"),
        legend.text  = element_text(size = 14),
        legend.background = element_blank(),
        plot.margin = margin(0,0,0,0))   +
  #guides(color = FALSE)+
  scale_x_continuous(breaks = 1:12, limits = c(1,12)) + #
  #scale_x_discrete(expand = c(0.02,0)) +
  #scale_y_continuous(expand = c(0.02,0)) +
  annotate("text", x = 1.8, y = 172.5, label = "A", fontface = "bold", size = 10)


## upload SMAP
smap_9km <- read.csv(here("data","raw", "public", "SMAP_monthly_HR_means_2016_2023.csv"))

fig_1_b_sm <- smap_9km %>% 
  rename(region = HR_NAME,
         smap = mean) %>% 
  group_by(region, month) %>% 
  summarise(mean = mean(smap, na.rm = TRUE)) %>% 
  mutate(month = factor(as.numeric(month)), levels = 1:12, labels = month.abb) %>% 
  ggplot(aes(x = month, y = mean, color = region, group = region)) +
  geom_line(size = 1.5) +
  geom_point(size = 4) +
  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005")) +
  labs(y = "Soil Moisture (m³/m³)", color = "Hydrologic Region", x = NULL) +
  theme_bw() +
  theme(#legend.position =c(0.55,.59), 
        axis.title = element_text(size = 15, face = "bold"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        panel.grid = element_blank(),
        legend.title = element_text(size = 17, face = "bold"),
        legend.text  = element_text(size = 16),
        plot.margin = margin(0,0,0,0)) +
  guides(color = FALSE) #+
  #scale_x_discrete(expand = c(0.02, 0.1)) # +
  #scale_y_continuous(expand = c(0.02,0)) +
  #annotate("text", x = 1.8, y = 170, label = "B", fontface = "bold", size = 10)
  

## upload ET (openET)

openet <- read.csv(here("data","raw", "public", "OpenET_monthly_HR_means_2021_2023.csv"))

fig_1_c_et <- openet %>% 
  rename(region = HR_NAME,
         openet = mean) %>% 
  group_by(region, month) %>% 
  summarise(mean = mean(openet, na.rm = TRUE)) %>% 
  mutate(month = factor(as.numeric(month)), levels = 1:12, labels = month.abb) %>% 
  ggplot(aes(x = month, y = mean, color = region, group = region)) +
  geom_line(size = 1.5) +
  geom_point(size = 4) +
  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005")) +
  labs(y = "Evapotranspiration (mm)", color = "Hydrologic Region", x = NULL) +
  theme_bw() +
  theme(#legend.position =c(0.55,.59), 
        axis.title = element_text(size = 15, face = "bold"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        panel.grid = element_blank(),
        legend.title = element_text(size = 17, face = "bold"),
        legend.text  = element_text(size = 16),
        plot.margin = margin(0,0,0,0)) +
  guides(color = FALSE) #+
  scale_x_discrete(expand = c(0.02, 0.1))# +
  #scale_y_continuous(expand = c(0.02,0)) +
  annotate("text", x = 1.8, y = 170, label = "B", fontface = "bold", size = 10)

  
  
### combine them

# split into top/bottom rows
bottom_row <- (fig_1_c | plot_spacer()| fig_1_d ) +
  plot_layout(widths = c(1, 0.04, 1))  # tiny gap

top_row <- fig_1_a_pp | fig_1_b_sm | fig_1_c_et

fig_1_full <- top_row / bottom_row +
  plot_layout(heights = c(0.8, 2))

ggsave(fig_1_full, file = here("outputs", "figures", "main", "fig_1_full_v2.png"), 
       dpi = 400, bg = "white",
       width = 12, height = 12)
```


## Figure 2

### Part A - Trap stations
format data
```{r}
### correct crs
#target_crs <- 3310
#ca_3310 <- ca %>% st_transform(target_crs)
#cv_3310 <- st_transform(cv, target_crs)
#
#
### upload station data
#stations_all <- read.csv(here("data", "interim", "cluster_all_info.csv")) %>% 
#  dplyr::select(-X) %>% 
#  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta")
#
#cluster_summary <- stations_all %>% 
#  group_by(cluster_id) %>% 
#  summarise(n_traps = n_distinct(trapstation_id),
#            lat = mean(latitude, na.rm = TRUE),
#            lon = mean(longitude, na.rm = TRUE), .groups = "drop") %>% 
#  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>% 
#  st_transform(target_crs)
#
#cluster_summary_cv <- st_intersection(cluster_summary, cv_3310)
#
```

plot data
```{r}

#fig_2_a <- ggplot() +
#  geom_sf(data = ca_3310, fill = "grey80", color = "grey50", size = 0.3) +
#  geom_sf(data = cv_3310, fill = "grey99", color = "black", size = 0.6, alpha = 0.5) +
#  geom_sf(data = cluster_summary_cv, aes(color = log(n_traps)), alpha = 0.7) +
#  scale_color_paletteer_c("grDevices::Blue-Yellow", direction = 1) +
#  labs(color  = "log(Traps per Cluster)") +
#  theme_style +
#  theme(legend.position =c(0.1,.15),
#        legend.text = element_text(size = 15),
#        legend.title = element_text(size = 14, face = "bold")) +
#  coord_sf(xlim = c(-122.7, -118.4), ylim = c(34.7, 40.4), crs = 4326, expand = FALSE) +
#  annotate("text", x = -120.5, y = 40, label = "A", fontface = "bold", size = 10) +
#  annotation_scale(location = "tr", width_hint = 0.22, pad_x = unit(.2, "cm"), pad_y = unit(.2, "cm")) #+
#  annotation_north_arrow(location = "tr",  pad_x = unit(.2, "cm"), pad_y = unit(1.2, "cm"))
#
#ggsave(fig_2_a, file = here("outputs", "figures", "main", "fig_2_a_v2.png"), dpi = 400, bg = "white")
```


### Part C - Abundance
format data
```{r}
### upload data
#abundance_tar_cluster <- read.csv(here("data", "interim", "abundance_tar_cluster.csv")) %>% 
#  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% #
#  rename(year = surv_year)
#
### make summary 
#abundance_summary <- abundance_tar_cluster %>% 
#  group_by(year, month) %>% 
#  summarise(mean_mos = mean(mos_per_trap_night, na.rm = TRUE),
#            sd_mos = sd(mos_per_trap_night, na.rm = TRUE),
#            n = n(), .groups = "drop") %>% 
#  mutate(year_num = as.numeric(year),
#         month_num = as.numeric(month),
#         time_id = year_num + (month_num-1)/12,
#         lower = pmax(mean_mos - sd_mos,0),
#         upper = pmax(mean_mos + sd_mos, 100),
#         mean_mos_log = log(mean_mos+1)) %>% 
#  filter(time_id >= (2003 + (4-1)/12),
#         time_id <= (2023 + (11-1)/12))
#
### pdsi data
#pdsi <- read.csv(here("data", "interim", "covariates_scalelag_stationmeta.csv")) %>% 
#  dplyr::select(county, cluster_id, year, month, pdsi_raw) %>% 
#  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta")
#
#pdsi_summary <- pdsi %>% 
#  filter(year >= 2003, year <= 2023) %>% 
#  mutate(date = as.Date(sprintf("%d-%02d-01", year, month))) %>% 
#  group_by(year, month) %>% 
#  summarise(pdsi_mean = mean(pdsi_raw, na.rm = TRUE), .groups = "drop") %>% 
#  mutate(year_num = as.numeric(year),
#         month_num = as.numeric(month),
#         time_id = year_num + (month_num - 1)/12,
#         xmin = time_id - 1/24, #year_num - 0.5,
#         xmax = time_id + 1/24) #year_num + 0.5) 

```

plot data
```{r}
#fig_2_b <- ggplot() +
#  geom_rect(data = pdsi_summary, aes(xmin = xmin, xmax = xmax,
#                                     ymin = -Inf, ymax = Inf,
#                                     fill = pdsi_mean), alpha = 0.3) +
#  
#  geom_line(data = abundance_summary, aes(x = time_id, y = mean_mos_log), color =  "#0047ab", linewidth #= 1) +
#  geom_point(data = abundance_summary, aes(x = time_id, y = mean_mos_log), color = "#007fff", size = #2.5) +
#  
#  scale_fill_gradient2(low = "#9E3D22", mid = "white", high = "#2B5C8A", midpoint = 0,
#                       name = "Annual\nMean\nPDSI") +
#  scale_x_continuous(breaks = seq(min(abundance_summary$time_id), max(abundance_summary$time_id), by = #1),
#                     labels = function(x) ifelse(x %% 4 ==3, x, ""), expand = c(0,0.0)) +
#  labs(y = "log(Mosquitoes per trap night)") +
#  theme_classic(base_size = 14) +
#  theme(axis.title.x = element_blank(),
#    axis.title.y = element_text(face = "bold"),
#    legend.title = element_text(face = "bold"),
#    plot.margin = margin(0, 0, 0, 1)) +
#  annotate("text", x = 2004, y = 5, label = "B", fontface = "bold", size = 10) +
#  coord_cartesian(clip = "off")

```


### Part C - WNV MIR
format data
```{r}
### upload data
#wnv_tar_cluster <- read.csv(here("data", "interim", "wnv_tar_cluster.csv")) %>% 
#  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% #
#  rename(year = surv_year)
#
### make summary 
#wnv_summary <- wnv_tar_cluster %>% 
#  group_by(year, month) %>% 
#  summarise(mean_wnv = mean(WNV_MIR, na.rm = TRUE),
#            sd_wnv = sd(WNV_MIR, na.rm = TRUE),
#            n = n(), .groups = "drop") %>% 
#  mutate(year_num = as.numeric(year),
#         month_num = as.numeric(month),
#         time_id = year_num + (month_num-1)/12,
#         lower = pmax(mean_wnv - sd_wnv,0),
#         upper = pmax(mean_wnv + sd_wnv, 100),
#         mean_wnv_log = log(mean_wnv+1)) %>% 
#  filter(time_id >= (2003 + (4-1)/12),
#         time_id <= (2023 + (11-1)/12))
#
```

plot data
```{r}
#fig_2_c <- ggplot() +
#  geom_rect(data = pdsi_summary, aes(xmin = xmin, xmax = xmax,
#                                     ymin = -Inf, ymax = Inf,
#                                     fill = pdsi_mean), alpha = 0.3) +
#  
#  geom_line(data = wnv_summary, aes(x = time_id, y = mean_wnv_log), color =  "#0047ab", linewidth = 1) #+
#  geom_point(data = wnv_summary, aes(x = time_id, y = mean_wnv_log), color = "#007fff", size = 2.5) +
#  
#  scale_fill_gradient2(low = "#9E3D22", mid = "white", high = "#2B5C8A", midpoint = 0,
#                       name = "Mean PDSI") +
#  scale_x_continuous(breaks = seq(2003, 2023, by = 3),
#                     labels = function(x) x, expand = c(0,0)) + 
#  labs(y = "log(WNV MIR)") +
#  theme_classic(base_size = 14) +
#  theme(axis.title.x = element_blank(),
#        legend.text = element_text(size = 15),
#        legend.title = element_text(size = 14, face = "bold"),
#        legend.key.width = unit(0.8, "cm"),
#    axis.title.y = element_text(face = "bold"),
#    plot.margin = margin(0, 0, 0, 1)) +
#  annotate("text", x = 2004, y = 2.5, label = "C", fontface = "bold", size = 10) +
#  coord_cartesian(clip = "off")
#

```

**Combine for full Fig 2**
```{r}
#fig_2_a_v2 <- fig_2_a + theme(legend.position = "bottom")  
#fig_2_b_v2 <- fig_2_b + guides(fill = FALSE) + theme(axis.text.x = element_blank())
#fig_2_c_v2 <- fig_2_c + theme(legend.position = "bottom", axis.text.x = element_text(size = 14)) ##guides(fill = FALSE)
#
#
#fig_2_full <- fig_2_a_v2 | (fig_2_b_v2 / fig_2_c_v2) 
#
#
#ggsave(fig_2_full, file = here("outputs", "figures", "main", "fig_2_full_v1.png"), 
#       dpi = 400, bg = "white", width = 11)
#
```



## Figure 3

### Part A - Overall effect of PDSI
format data
```{r}
## upload model results
mod_fe_abund_pdsi <- readRDS(here("outputs", "models", "mod_fe_abund_pdsi.rds"))
mod_fe_wnv_pdsi <- readRDS(here("outputs", "models", "mod_fe_wnv_pdsi.rds"))

## make one 
abund_pdsi_coef <- broom::tidy(mod_fe_abund_pdsi) %>% 
  filter(term == "pdsi_lag0") %>% 
  mutate(outcome = "Abundance")

wnv_pdsi_coef <- broom::tidy(mod_fe_wnv_pdsi) %>% 
  filter(term == "pdsi_lag0") %>% 
  mutate(outcome = "WNV MIR")
  
pdsi_coef <- bind_rows(abund_pdsi_coef, wnv_pdsi_coef)
```

plot data
```{r}
fig_3_a <- pdsi_coef %>% 
  ggplot(aes(x = outcome, y = estimate, color = outcome)) +
  geom_errorbar(aes(ymin = estimate - 1.96 * std.error,
                    ymax = estimate + 1.96 * std.error),width = 0.15, linewidth = 2) +
  geom_point(size = 6.5) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 1, color = "grey10") +
  scale_color_manual(values = c( "Abundance" = "#007fff", "WNV MIR" ="#007fff" )) +# "#0047ab""#098154"
  theme_classic(base_size = 18) +
  #theme_minimal(base_size = 18) +
  labs(x = "",y = "Effect of PDSI") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.position = "none") #+
  annotate("text", x = .5, y = 0.18, label = "A", fontface = "bold", size = 10)

#ggsave(fig_3_a, file = here("outputs", "figures", "main", "fig_3_a_v1.png"), dpi = 400, bg = "white")
```

### Part B - Spatial heterogeneity of PDSI
format data
```{r}
mod_fe_abund_pdsi_HR <- readRDS(here("outputs", "models", "mod_fe_abund_pdsi_HR.rds"))
mod_fe_wnv_pdsi_HR <- readRDS(here("outputs", "models", "mod_fe_wnv_pdsi_HR.rds"))

abund_pdsi_HR_coef <- broom::tidy(mod_fe_abund_pdsi_HR) %>% 
  mutate(outcome = "Abundance")  %>% 
  filter(grepl("hydro_region::", term)) %>% 
  mutate(hydro_region = gsub("hydro_region::", "", term),
         hydro_region = gsub("HR:pdsi_lag0", "", hydro_region),
         lower = estimate - 1.96 * std.error,
         upper = estimate + 1.96 * std.error)

wnv_pdsi_HR_coef <- broom::tidy(mod_fe_wnv_pdsi_HR) %>% 
  mutate(outcome = "WNV MIR")  %>% 
  filter(grepl("hydro_region::", term)) %>% 
  mutate(hydro_region = gsub("hydro_region::", "", term),
         hydro_region = gsub("HR:pdsi_lag0", "", hydro_region),
         lower = estimate - 1.96 * std.error,
         upper = estimate + 1.96 * std.error) 

pdsi_HR_coef <- bind_rows(abund_pdsi_HR_coef, wnv_pdsi_HR_coef) 
```

plot data
```{r}
fig_3_b <- pdsi_HR_coef %>% 
  ggplot(aes(x = outcome, y = estimate, color = hydro_region)) +
  geom_errorbar(aes(ymin = estimate - 1.96 * std.error,
                    ymax = estimate + 1.96 * std.error),width = 0.35, linewidth = 2,
                position = position_dodge(width = 0.65)) +
  geom_point(size = 6.5,position = position_dodge(width = 0.65)) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005" )) +
  theme_classic(base_size = 18) +
  #theme_minimal(base_size = 18) +
  labs(x = "",y = "Effect of PDSI", color = "Hydrological Region") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.title = element_text(face = "bold"),
    legend.position = "right") +
  annotate("text", x = .5, y = 0.33, label = "B", fontface = "bold", size = 10)

#ggsave(fig_3_b, file = here("outputs", "figures", "main", "fig_3_b_v1.png"), dpi = 400, bg = "white")
```


### Part C - Hydrological variable associations
format data
```{r}
## upload model results
mod_fe_abund_hydro_withlags <- readRDS(here("outputs", "models", "mod_fe_abund_hydro_withlags.rds"))
mod_fe_wnv_hydro_withlags <- readRDS(here("outputs", "models", "mod_fe_wnv_hydro_withlags.rds"))

## make into tables
abund_hydro_coef <- map2_df(mod_fe_abund_hydro_withlags, names(mod_fe_abund_hydro_withlags), ~ {
  tidy(.x) %>%
    filter(term == .y) %>%   # match the variable to its model
    mutate(hydro_var = .y,
           outcome = "Abundance")
})

wnv_hydro_coef <- map2_df(mod_fe_wnv_hydro_withlags, names(mod_fe_wnv_hydro_withlags), ~ {
  tidy(.x) %>%
    filter(term == .y) %>%   # match the variable to its model
    mutate(hydro_var = .y,
           outcome = "WNV MIR")
})


both_hydro_coef <- bind_rows(abund_hydro_coef, wnv_hydro_coef) %>% 
  mutate(lag = case_when(grepl("lag0", term) ~ "0 mo",
                         grepl("lag1", term) ~ "1 mo",
                         grepl("lag2", term) ~ "2 mo",
                         grepl("lag3", term) ~ "3 mo",
                         TRUE ~ NA_character_)) %>% 
  mutate(hydro_var = case_when(grepl("soilmoisture", hydro_var) ~ "Soil Moisture",
                               grepl("et", hydro_var) ~ "Evapotranspiration",
                               grepl("jrc_5km", hydro_var) ~ "Surface Water", #Standing 
                               grepl("jrc_10km", hydro_var) ~ "Surface Water (10km)",
                               TRUE ~ NA_character_))

#write.csv(both_hydro_coef, here("outputs", "models", "both_hydro_coef.csv"), row.names = FALSE)
```

plot data
```{r}
hydro_colors <- c(  
  "Soil Moisture" =     "#D3105C" , 
  "Evapotranspiration" = "#3A5D3D",
  "Surface Water" =  "#4C4976", #Standing 
  "Surface Water (10km)" = "#D87B82") #Standing 

lag_alpha <- c("0 mo" = 1,
               "1 mo" = 0.75,
               "2 mo" = 0.55,
               "3 mo" = 0.35)

fig_3_c <- both_hydro_coef %>% 
  filter(hydro_var != "Surface Water (10km)") %>% #Standing
  mutate(hydro_var = factor(hydro_var,
                               levels = c("Soil Moisture","Surface Water", "Evapotranspiration" ))) %>% #Standing 
  ggplot(aes(x = outcome, y = estimate, color = hydro_var, alpha = lag)) +
  geom_errorbar(aes(ymin = estimate - 1.96 * std.error,
                    ymax = estimate + 1.96 * std.error),width = 0.35, linewidth = 2,
                position = position_dodge(width = 0.65)) +
  geom_point(size = 4.5,position = position_dodge(width = 0.65)) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 1, color = "grey10") +
  scale_color_manual(values = c(hydro_colors)) +
  scale_alpha_manual(values = lag_alpha) +
  theme_classic(base_size = 18) +
  #theme_minimal(base_size = 18) +
  labs(x = "",y = "Coefficient Estimate", alpha = "Month Lag") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.title = element_text(face = "bold"),
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 20)) +
  facet_wrap(~hydro_var, ncol = 3) +
  guides(color = FALSE) + 
  geom_vline(xintercept = 1.5, color = "grey85", linetype = "dotted")

```


**Combine for full Fig 3**
```{r}
#fig_3_a_v2 <- fig_3_a_ +
#  annotate("text", x = .5, y = 0.18, label = "A", fontface = "bold", size = 10)
#
#fig_3_b_v2 <-  fig_3_b +
#  annotate("text", x = .5, y = 0.33, label = "B", fontface = "bold", size = 10)
#
#fig_3_c_v2 <- fig_3_c + theme(legend.position = "right")
#
#fig_3_full <- (fig_3_a + fig_3_b)/ fig_3_c_v2 +
#  plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 28, face = "bold"))
#
#ggsave(fig_3_full, file = here("outputs", "figures", "main", "fig_3_full_v3.png"),
#       width = 13, height = 10, 
#       dpi = 400, bg = "white")
#
```

another version of the combined figure (erin & alex's suggestions)
```{r}
## standardize y-axis & add grey dashed line
fig_3_a_v3 <- fig_3_a + scale_y_continuous(limits = c(-0.13, 0.31)) + geom_vline(xintercept = 1.5, color = "grey85", linetype = "dotted")
fig_3_b_v3 <- fig_3_b + scale_y_continuous(limits = c(-0.13, 0.31)) + geom_vline(xintercept = 1.5, color = "grey85", linetype = "dotted")

# move legend to right to match top row 
fig_3_c_v3 <- fig_3_c + theme(legend.position = "right")

# plot them together
fig_3_full <- (fig_3_a_v3 + fig_3_b_v3)/ fig_3_c_v3 +
  plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 28, face = "bold"))

ggsave(fig_3_full, file = here("outputs", "figures", "main", "fig_3_full_v5.png"),
       width = 13, height = 10, 
       dpi = 400, bg = "white")
```



# Supplemental Text

## Figure S1
format data
```{r}
### get everything in the correct crs
#target_crs <- 3310
#cv_3310 <- st_transform(cv, target_crs)
#
### rivers 
#rivers_major <- st_read(here("data","raw", "public", "NHD_Major_Rivers","NHD_Major_Rivers.shp" )) %>% 
#  st_zm(drop = TRUE) %>% 
#  st_transform(target_crs)
#
## only select rivers within central valley
#rivers_major_cv <- st_intersection(rivers_major, cv_3310) 
#
#rivers_major_rank <- rivers_major_cv %>% 
#  mutate(type_rank = case_when(ftype == 334 ~ "Connector",
#                               ftype == 336 ~ "Canal ditch",
#                               ftype == 428 ~ "Pipeline",
#                               ftype == 460 ~ "Stream/river",
#                               ftype == 558 ~ "Artificial path",
#                               TRUE ~ NA))   %>% #rivers_major %>% 
#  mutate(stablility_rank = case_when(fcode == 46006 ~ 5,          # Perennial
#                                     fcode == 46003 ~ 4,          # Intermittent
#                                     fcode %in% c(33600, 33601, 33400) ~ 3,  # Canal/Ditch
#                                     fcode == 55800 ~ 2,          # Artificial Path
#                                     TRUE ~ 1))                      # Ephemeral / Connector / Other)) # 
#
#
### wetlands
#wetlands <- st_read(here("data","raw", "public", "wetlands_cv.gpkg"), layer = "CA_Wetlands") %>%
#  st_transform(target_crs)
```

plot data
```{r}
#fig_s_1 <- ggplot() +
#  geom_sf(data = ca, fill = "grey97", color = NA, size = 0.3) +
#  geom_sf(data = cv_3310, fill = "grey85", color = "black", size = 0.6) +
#  # add water features
#  geom_sf(data = rivers_major_rank, aes(color = factor(type_rank)),  linewidth = 0.8) +
#  geom_sf(data = wetlands, aes(fill = WETLAND_TYPE), color = scales::alpha("black", 0.01), linewidth = #0.1) +
#  # assign colors
#  scale_fill_manual(values = c("Freshwater Emergent Wetland" = "#F11B00",
#                               "Freshwater Forested/Shrub Wetland" = "#EE5A03",
#                               "Freshwater Pond" =  "#EA8005",         
#                               "Riverine" = "#DFBF2B",              
#                               "Lake" = "#F2B705",                         
#                               "Estuarine and Marine Wetland" = "#ADC397",
#                               "Estuarine and Marine Deepwater" = "#95BBB1",
#                               "Other" =  "#CAC96A")) +
#    scale_color_manual(values = c("Stream/river" = "#08519c",  
#                                "Canal ditch"    = "#4F94F7",   
#                                "Connector"      = "#5780D1",   
#                                "Artificial path"= "#58ADC5",   
#                                "Pipeline"       = "#7bccc4")) +
#  guides(color = guide_legend(override.aes = list(linewidth = 4)))+
#  theme_style +
#  theme(legend.text = element_text(size = 15),
#        legend.title = element_text(size = 14, face = "bold"))  +
#  labs(fill = "Wetland Type", color = "River Type") +
#  coord_sf(xlim = c(-122.7, -118.4), ylim = c(34.7, 40.4), crs = 4326, expand = FALSE) 
#
#ggsave(fig_s_1, file = here("outputs", "figures", "supplement", "fig_s_1_v1.png"), dpi = 400, bg = #"white")
```


## Figure S2
```{r}
### upload data
#stations_all <- read.csv(here("data", "interim", "cluster_all_info.csv")) %>% 
#  dplyr::select(-X) %>% 
#  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta")
#
### format data
#fig_s_2 <- stations_all %>% 
#  group_by(cluster_id) %>% 
#  summarise(n_traps = n_distinct(trapstation_id)) %>% 
#  ungroup() %>% 
#  ggplot(aes(x = n_traps)) +
#  geom_histogram(binwidth = 1, fill = "#007fff", color = "#606372") + #"#79A8A4"
#  labs(x = "Number of trap stations per cluster", y = "Count of clusters") +
#  theme_minimal() +
#  xlim(c(0,100)) +
#  theme(axis.title = element_text(size = 14, face = "bold")) 
#
#ggsave(fig_s_2, file = here("outputs", "figures", "supplement", "fig_s_2_v1.png"), dpi = 400, bg = #"white")
```

## Figure S3

### Part A - full map of CA
```{r}
### correct crs
#target_crs <- 3310
#ca_3310 <- ca %>% st_transform(target_crs)
#cv_3310 <- st_transform(cv, target_crs)
#
#
### upload station data
#stations_all <- read.csv(here("data", "interim", "cluster_all_info.csv")) %>% 
#  dplyr::select(-X) %>% 
#  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta")
#
#cluster_summary <- stations_all %>% 
#  group_by(cluster_id) %>% 
#  summarise(n_traps = n_distinct(trapstation_id),
#            lat = mean(latitude, na.rm = TRUE),
#            lon = mean(longitude, na.rm = TRUE), .groups = "drop") %>% 
#  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>% 
#  st_transform(target_crs)
#
#cluster_summary_cv <- st_intersection(cluster_summary, cv_3310)
#
#
#fig_s_3_a <- ggplot() +
#  geom_sf(data = ca_3310, fill = "grey80", color = "grey50", size = 0.3) +
#  geom_sf(data = cv_3310, fill = "grey99", color = "black", size = 0.6, alpha = 0.5) +
#  geom_sf(data = cluster_summary_cv, aes(color = log(n_traps)), alpha = 0.7) +
#  scale_color_paletteer_c("grDevices::Blue-Yellow", direction = 1) +
#  labs(color  = "log(Traps\nper\nCluster)") +
#  theme_style +
#  theme(#legend.position =c(0.1,.15),
#        legend.text = element_text(size = 15),
#        legend.title = element_text(size = 14, face = "bold")) +
#  #annotate("text", x = -120.5, y = 40, label = "A", fontface = "bold", size = 10) +
#  annotation_scale(location = "tr", width_hint = 0.22, pad_x = unit(.2, "cm"), pad_y = unit(.2, "cm")) #+
#  annotation_north_arrow(location = "tr",  pad_x = unit(.2, "cm"), pad_y = unit(1.2, "cm"))
```

### Part B - hydrological regions
format data
```{r}
### upload data
counties_sac <- c("Butte", "Glenn", "Colusa", "Yolo", "Sacramento",
                  "Placer", "Yuba", "Shasta", "Tehama", "Sutter", "Shasta")
counties_sanjoaquin <- c("San Joaquin", "Stanislaus", "Merced","Madera", "Fresno")
counties_tulare <- c("Kings", "Tulare", "Kern")

county_to_hr <- dplyr::bind_rows(data.frame(county = counties_sac, hydro_region = "Sacramento River #HR"),
  data.frame(county = counties_sanjoaquin,hydro_region = "San Joaquin River HR"),
  data.frame(county = counties_tulare,hydro_region = "Tulare Lake HR"))


### select for largish cities
#cities <- maps::us.cities %>%
#  filter(country.etc == "CA", pop > 100000) %>%   # adjust threshold
#  st_as_sf(coords = c("long", "lat"), crs = 4326) %>%
#  st_transform(st_crs(ca_3310)) %>% 
#  mutate(name = sub(" CA$", "", name)) %>% 
#  st_intersection(cv_3310)
#
### add hydroregion
#cluster_summary_cv_HR <- cluster_summary_cv %>% 
#  mutate(county = gsub("_.*", "", cluster_id)) %>% 
#  left_join(county_to_hr, by = "county")
#
```

plot data 
(this needs work)
```{r}
#color_limits <- range(log(cluster_summary_cv_HR$n_traps), na.rm = TRUE)
#
#hr_list <- c("Sacramento River HR", "San Joaquin River HR", "Tulare Lake HR")
#
#HR_maps <- list()
#
#for(cty in hr_list) {
#  
#  county_clusters <- cluster_summary_cv_HR %>% 
#    filter(hydro_region == cty)
#  
#  # get bbox for zoom
#  bbox <- st_bbox(county_clusters)
#  
#  # make sac + tulare a little more zoomed out
#  xrange <- bbox["xmax"] - bbox["xmin"]
#  yrange <- bbox["ymax"] - bbox["ymin"]
#  
#  if(cty %in% c("Sacramento River HR", "Tulare Lake HR")) {
#    xpad <- xrange * 0.5
#    ypad <- yrange * 0.5
#    } else {
#    xpad <- xrange * 0.15
#    ypad <- yrange * 0.15
#  }
#  
#  # crop cities to region
#  bbox_expanded <- bbox
#
#  bbox_expanded["xmin"] <- bbox["xmin"] - xpad
#  bbox_expanded["xmax"] <- bbox["xmax"] + xpad
#  bbox_expanded["ymin"] <- bbox["ymin"] - ypad
#  bbox_expanded["ymax"] <- bbox["ymax"] + ypad
#
#  cities_sub <- st_crop(cities, bbox_expanded)
#  
#  # plot
#  fig_s_clusterlocation_cty <- ggplot() +
#    
#    geom_sf(data = ca_3310, 
#            fill = "grey90", 
#            color = "white") +
#    
#    geom_sf(data = county_clusters, 
#            aes(color = log(n_traps)), 
#            alpha = .3) +
#    
#    geom_sf_text(data = cities_sub, aes(label = name, geometry = geometry), 
#                 stat = "sf_coordinates",
#                 force = 2, color = "red", size = 6) +
#    
#    scale_color_gradientn(colors = paletteer_c("grDevices::Purple-Yellow", 30),
#                          limits = color_limits) +
#    
#    coord_sf(xlim = c(bbox_expanded["xmin"],
#                      bbox_expanded["xmax"]),
#             ylim = c(bbox_expanded["ymin"],
#                      bbox_expanded["ymax"]), expand = FALSE)+
#    
#    theme_style +
#    theme(title = element_text(size = 15, face = "bold"),
#      legend.title = element_text(size = 14, face = "bold"),
#      legend.text = element_text(size = 13)) +
#    
#    labs(color = "log(Traps per Cluster)", title = cty)
#  
#  # store in list
#  HR_maps[[cty]] <- fig_s_clusterlocation_cty
#}
#
### make individual plots
#fig_s_3_b <- HR_maps[["Sacramento River HR"]] + guides(color = FALSE)
#
#fig_s_3_c <- HR_maps[["San Joaquin River HR"]] + guides(color = FALSE)
#
#fig_s_3_d <- HR_maps[["Tulare Lake HR"]] + guides(color = FALSE)
```

**Combine for full Figure**
```{r}
## combine plots
#fig_s_3_full <- (fig_s_3_a + fig_s_3_b) / (fig_s_3_c + fig_s_3_d)
#
#ggsave(fig_s_3_full, file = here("outputs", "figures", "supplement", "fig_s_3_full_v1.png"), 
#       dpi = 400, bg = "white",
#       width = 12, height = 12)
```

## Figure S4
format data
```{r}

### upload data
abundance_all_cluster <- read.csv(here("data", "interim", "abundance_all_cluster.csv")) %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% #
  rename(year = surv_year)

## make summary 
abundance_all_summary <- abundance_all_cluster %>% 
  group_by(county, year, month, species) %>% 
    summarise(n_traps = n_distinct(trapstation_id),
      total_mos = sum(num_clean, na.rm = TRUE),
      total_trap_nights = sum(trap_nights, na.rm = TRUE),
      mos_per_trap_night = total_mos / total_trap_nights,
      .groups = "drop") %>% 
  mutate(mos_per_trap_night_log = log(mos_per_trap_night+1))
```

plot data
```{r}
## colors
pal_dar3 <- wes_palette("Darjeeling1", 3, type = "continuous")

fig_s_4 <- abundance_all_summary %>% 
  filter(species == "Cx tarsalis") %>% 
  #filter(species != "Cx pipiens/restuans/salinarius") %>% 
  ggplot(aes(x = as.integer(year), y = mos_per_trap_night_log)) +
  geom_point(alpha = .1, color = "#F2AD00") + 
  #geom_point(aes(color = species),alpha = .1) + 
  #scale_color_manual(values = rev(pal_dar3)) +
  geom_smooth( linewidth = 1.2) +
  facet_wrap(~county, scales = "free_y") +
  theme_classic(base_size = 13) +
  labs(y = "log(mosquitioes/trap night+1)", color = "Species") +
  guides(color = guide_legend(override.aes = list(alpha = 1))) + 
  theme(axis.title.y = element_text(size = 14, face = "bold"),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        legend.title = element_text(size = 14, face = "bold"),
        legend.text = element_text(size = 14),
        strip.background = element_rect(fill = "grey30", color = NA),
        strip.text = element_text(color = "white", face = "bold")) +
  scale_x_continuous(breaks = seq(2003,2023, by = 4), limits = c(2003,2023), labels = function(x) substr(x, 3,4)) 

ggsave(fig_s_4, file = here("outputs", "figures", "supplement", "fig_s_4_v2.png"), 
       dpi = 400, bg = "white")

```


## Figure S5
format data
```{r}

## upload data
wnv_all_cluster <- read.csv(here("data", "interim", "wnv_all_cluster.csv")) %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% #
  rename(year = surv_year)

## make summary 
wnv_all_summary <- wnv_all_cluster %>% 
  group_by(county, year, month, species) %>% 
    summarise(n_traps = n_distinct(trapstation_id),
              total_pools = n(),
              positive_pools = sum(test_status == "Confirmed", na.rm = TRUE),
              total_mos_tested = sum(num_clean, na.rm = TRUE),
              WNV_MIR = ifelse(total_mos_tested > 0,
                               (positive_pools / total_mos_tested)*1000, NA_real_), .groups = "drop") %>% 
  filter(WNV_MIR < 101) %>% 
  mutate(WNV_MIR_log = log(WNV_MIR+1))
```

plot data
```{r}
fig_s_5 <- wnv_all_summary %>% 
  filter(species == "Cx tarsalis") %>% 
  #filter(species != "Cx pipiens/restuans/salinarius") %>% 
  ggplot(aes(x = as.integer(year), y = WNV_MIR_log)) +
  geom_point(alpha = .1, color = "#F2AD00") + 
  #geom_point(aes(color = species), alpha = .1) + 
  scale_color_manual(values = rev(pal_dar3)) +
  geom_smooth( linewidth = 1.2) +
  facet_wrap(~county, scales = "free_y") +
  theme_classic(base_size = 13) +
  labs(y = "log(WNV MIR +1)", color = "Species") +
  guides(color = guide_legend(override.aes = list(alpha = 1))) + 
  theme(axis.title.y = element_text(size = 14, face = "bold"),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        legend.title = element_text(size = 14, face = "bold"),
        legend.text = element_text(size = 14),
        strip.background = element_rect(fill = "grey30", color = NA),
        strip.text = element_text(color = "white", face = "bold")) +
  scale_x_continuous(breaks = seq(2003,2023, by = 4), limits = c(2003,2023), labels = function(x) substr(x,3,4)) +
  coord_cartesian(ylim = c(0, NA))

ggsave(fig_s_5, file = here("outputs", "figures", "supplement", "fig_s_5_v2.png"), 
       dpi = 400, bg = "white")
```

## Figure S6

### Part A - soil moisture
```{r}
### upload data
## hydro region
#counties_sac <- c("Butte", "Glenn", "Colusa", "Yolo", "Sacramento",
#                  "Placer", "Yuba", "Shasta", "Tehama", "Sutter", "Shasta")
#counties_sanjoaquin <- c("San Joaquin", "Stanislaus", "Merced","Madera", "Fresno")
#counties_tulare <- c("Kings", "Tulare", "Kern")
#
#county_to_hr <- dplyr::bind_rows(data.frame(county = counties_sac, hydro_region = "Sacramento River #HR"),
#  data.frame(county = counties_sanjoaquin,hydro_region = "San Joaquin River HR"),
#  data.frame(county = counties_tulare,hydro_region = "Tulare Lake HR"))
#
## soil moisture
#soilmoisture <- read.csv(here("data", "interim", "covariate_soilmoisture_cluster.csv"))
#
#
#sm <- soilmoisture %>% 
#  mutate(year_month = as.Date(paste(year, month, 1, sep = "-"))) %>% 
#  mutate(county = gsub("_.*", "", cluster_id)) %>% 
#  left_join(county_to_hr, by = "county") 
#
#fig_s_6_a <- sm %>%  
#  filter(!is.na(hydro_region)) %>% 
#  ggplot(aes(x = year_month, y = soilmoisture, color = hydro_region)) +
#  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005" )) +
#  geom_smooth(linewidth = 1.5, fill = "grey90") +
#  theme_classic(base_size = 13) +
#  labs(y = "Soil Moisture (m³/m³)", color = "HR") +
#  guides(color = guide_legend(override.aes = list(alpha = 1))) + 
#  theme(axis.title.y = element_text(size = 14, face = "bold"),
#        axis.title.x = element_blank(),
#        legend.position = "bottom",
#        legend.title = element_text(size = 14, face = "bold"),
#        legend.text = element_text(size = 14),
#        #strip.background = element_rect(fill = "grey30", color = NA),
#        strip.text = element_text(color = "white", face = "bold")) +
#  scale_x_date(date_breaks = "4 years", date_labels = "%Y", expand = c(0,0)) +
#  annotate("text", x = as.Date("2004-01-01"), y = .27, label = "A", fontface = "bold", size = 10)
#  
```

### Part B - evapotranspiration
```{r}
### upload data
#
## evapotranspiration
#evapotranspiration <- read.csv(here("data", "interim", "covariate_et_cluster.csv"))
#
#
#et <- evapotranspiration %>% 
#  mutate(year_month = as.Date(paste(year, month, 1, sep = "-"))) %>% 
#  mutate(county = gsub("_.*", "", cluster_id)) %>% 
#  left_join(county_to_hr, by = "county") 
#
#fig_s_6_b <- et %>%  
#  filter(!is.na(hydro_region)) %>% 
#  ggplot(aes(x = year_month, y = ET_mm, color = hydro_region)) +
#  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005" )) +
#  geom_smooth(linewidth = 1.5, fill = "grey90") +
#  theme_classic(base_size = 13) +
#  labs(y = "Evapotranspiration (mm)", color = "HR") +
#  guides(color = guide_legend(override.aes = list(alpha = 1))) + 
#  theme(axis.title.y = element_text(size = 14, face = "bold"),
#        axis.title.x = element_blank(),
#        legend.position = "bottom",
#        legend.title = element_text(size = 14, face = "bold"),
#        legend.text = element_text(size = 14),
#        #strip.background = element_rect(fill = "grey30", color = NA),
#        strip.text = element_text(color = "white", face = "bold")) +
#  scale_x_date(date_breaks = "4 years", date_labels = "%Y", expand = c(0,0)) +
#  annotate("text", x = as.Date("2004-01-01"), y = 34, label = "B", fontface = "bold", size = 10)
#  
```

### Part C - Standing water (within 5 km)
```{r}
### upload data
#
## evapotranspiration
#jrc_5km <- read.csv(here("data", "interim", "covariate_jrc5km_cluster.csv"))
#
#
#sw_5km <- jrc_5km %>% 
#  mutate(year_month = as.Date(paste(year, month, 1, sep = "-"))) %>% 
#  mutate(county = gsub("_.*", "", cluster_id)) %>% 
#  left_join(county_to_hr, by = "county") 
#
#fig_s_6_c <- sw_5km %>%  
#  filter(!is.na(hydro_region)) %>% 
#  ggplot(aes(x = year_month, y = jrc_5km, color = hydro_region)) +
#  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005" )) +
#  geom_smooth(linewidth = 1.5, fill = "grey90") +
#  theme_classic(base_size = 13) +
#  labs(y = "Standing Water (%)", color = "HR") +
#  guides(color = guide_legend(override.aes = list(alpha = 1))) + 
#  theme(axis.title.y = element_text(size = 14, face = "bold"),
#        axis.title.x = element_blank(),
#        legend.position = "bottom",
#        legend.title = element_text(size = 14, face = "bold"),
#        legend.text = element_text(size = 14),
#        #strip.background = element_rect(fill = "grey30", color = NA),
#        strip.text = element_text(color = "white", face = "bold")) +
#  scale_x_date(date_breaks = "4 years", date_labels = "%Y", expand = c(0,0)) +
#  annotate("text", x = as.Date("2004-01-01"), y = 2.5, label = "C", fontface = "bold", size = 10)
#  
```

**Combine them for full Fig**
```{r}
#fig_s_6_full <- fig_s_6_a + fig_s_6_b + fig_s_6_c + plot_layout(guides = "collect") & #theme(legend.position = "bottom",
#                                                                            legend.direction = #"horizontal")
#
#ggsave(fig_s_6_full, file = here("outputs", "figures", "supplement", "fig_s_6_v1.png"), 
#       width = 12, height = 8,
#       dpi = 400, bg = "white")
```


## Figure S7
```{r}
## upload data
# bird competence index
bird <- read.csv(here("data", "interim", "covariate_bird_cluster.csv")) 

bird_comp <- bird %>% 
  mutate(year_month = as.Date(paste(year, month, 1, sep = "-"))) %>% 
  mutate(county = gsub("_.*", "", cluster_id)) %>% 
  left_join(county_to_hr, by = "county")  %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta")

#fig_s_7 <- bird_comp %>% 
#  filter(county != "Yuba") %>% 
#  ggplot(aes(x = year_month, y = log(bird_comp + 1))) +
#   geom_point(alpha = .1, color = "#F2AD00") + 
#  scale_color_manual(values = rev(pal_dar3)) +
#  geom_smooth( linewidth = 1.2) +
#  facet_wrap(~county, scales = "free_y") +
#  theme_classic(base_size = 13) +
#  labs(y = "log(Bird Index+1)") +
#  guides(color = guide_legend(override.aes = list(alpha = 1))) + 
#  theme(axis.title.y = element_text(size = 14, face = "bold"),
#        axis.title.x = element_blank(),
#        legend.position = "bottom",
#        legend.title = element_text(size = 14, face = "bold"),
#        legend.text = element_text(size = 14),
#        strip.background = element_rect(fill = "grey30", color = NA),
#        strip.text = element_text(color = "white", face = "bold")) +
#  scale_x_date(date_breaks = "4 years", date_labels = "%Y", expand = c(0,0))


#ggsave(fig_s_7, file = here("outputs", "figures", "supplement", "fig_s_7_v1.png"), 
#       dpi = 400, bg = "white")

## another version that erin suggested
pal_bigsur <- cal_palette(name = "bigsur", n = 16, type = "continuous")

fig_s_7 <- bird_comp %>% 
  filter(county != "Yuba") %>% 
  ggplot(aes(x = year_month, y = log(bird_comp + 1))) +
  geom_point(alpha = .08, size = 0.8, aes(color = county)) + 
  scale_color_manual(values = rev(pal_bigsur)) +
  #scale_color_manual(values = rev(pal_dar3)) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 30), linewidth = 1.5) +
  #facet_wrap(~county, scales = "free_y") +
  theme_classic(base_size = 13) +
  labs(y = "log(Bird Index+1)", color = "County") +
  guides(color = guide_legend(override.aes = list(alpha = 1))) + 
  theme(axis.title.y = element_text(size = 14, face = "bold"),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        legend.title = element_text(size = 14, face = "bold"),
        legend.text = element_text(size = 14),
        strip.background = element_rect(fill = "grey30", color = NA),
        strip.text = element_text(color = "white", face = "bold")) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y", expand = c(0,0)) +
  guides(color = guide_legend(nrow = 2, override.aes = list(alpha = 1, size = 3)))
  
ggsave(fig_s_7, file = here("outputs", "figures", "supplement", "fig_s_7_v2.png"), 
       dpi = 400, bg = "white", width = 10.5)
```
