---
title: "sensitivity_text"
output: html_document
---

Manuscript ID: RSTB-2025-0484

Title: Water availability affects West Nile virus dynamics in a heavily managed agricultural landscape

Authors: Samantha Sambado, Andrew J. MacDonald, Alex Konings, and Erin A. Mordecai

Corresponding author: ssambado@stanford.edu

```{r setup, include=FALSE}
library(here)
library(fixest)
library(broom)
library(purrr)
library(car)

## upload filtered panel data
abund_tar_panel_select <- read.csv(here("data", "derived", "abund_tar_panel_select.csv"))
wnv_tar_panel_select <- read.csv(here("data", "derived", "wnv_tar_panel_select.csv"))


## upload model results
#mod_fe_abund_pdsi <- readRDS(here("outputs", "models", "mod_fe_abund_pdsi.rds"))
#
#abund_pdsi_coef <- broom::tidy(mod_fe_abund_pdsi) %>% 
#  filter(term == "pdsi_lag0") %>% 
#  mutate(outcome = "Abundance")
#
#
##mod_fe_wnv_pdsi <- readRDS(here("outputs", "models", "mod_fe_wnv_pdsi.rds"))
#
#wnv_pdsi_coef <- broom::tidy(mod_fe_wnv_pdsi) %>% 
#  filter(term == "pdsi_lag0") %>% 
#  mutate(outcome = "WNV MIR")
#
#
##saveRDS(mod_fe_abund_pdsi_HR,file = here("outputs", "models", "mod_fe_abund_pdsi_HR.rds"))

counties_sac <- c("Butte", "Glenn", "Colusa", "Yolo", "Sacramento",
                  "Placer", "Yuba", "Shasta", "Tehama", "Sutter", "Shasta")

counties_sanjoaquin <- c("San Joaquin", "Stanislaus", "Merced","Madera", "Fresno")

counties_tulare <- c("Kings", "Tulare", "Kern")

county_to_hr <- dplyr::bind_rows(data.frame(county = counties_sac, hydro_region = "Sacramento River HR"),
  data.frame(county = counties_sanjoaquin,hydro_region = "San Joaquin River HR"),
  data.frame(county = counties_tulare,hydro_region = "Tulare Lake HR"))
```

# Supplemental Text

# Effect of PDSI
## Abundance
## Text S4

### S4.1-S4.2
```{r}
## build model 
mod_fe_abund_pdsi <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_select)

# check summaries
summary(mod_fe_abund_pdsi)
round(confint(mod_fe_abund_pdsi, level = 0.95),2)

# clean up
broom::tidy(mod_fe_abund_pdsi) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))
```

### S4.3.1
Tale of varying fixed effects
```{r}

mod_fe_abund_pdsi_csw <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             csw0(cluster_id, cluster_id + year, cluster_id + month, cluster_id + year + month),
                           vcov = conley(5),
                           data = abund_tar_panel_select)

etable(mod_fe_abund_pdsi_csw,
       headers = c("OLS", "Cluster FE", "Cluster + Month FE",
                   "Cluster + Year FE", "Cluster + Month + Year FE"),
       dict = c("log(mos_per_trap_night+1" = "Abundance",
                pdsi_lag0 = "PDSI",
                temp_lag0 = "Temp (std)",
                temp_lag0_sq = "Temp^2 (std)"),
       fitstat = ~ n + r2 + wr2,
        digits = 3, style.tex = style.tex("aer"))



```

### S4.3.2
Multicollinearity
```{r}
mod_ols_abund_pdsi <- lm(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) , data = abund_tar_panel_select)
vif(mod_ols_abund_pdsi)
```

(Robustness checks)
### S4.4.1 
Alternative fixed effects
```{r}
### format data
# set up dictionary
outcome <- "log(mos_per_trap_night + 1)"

covariates <- "pdsi_lag0 + temp_lag0 + I(temp_lag0^2)"

FE_list <- list("cluster + month + year" = ~cluster_id + month + year,
                "cluster + month" = ~cluster_id + month,
                "cluster + year" = ~cluster_id + year,
                "cluster" = ~cluster_id,
                "OLS" = NULL)


run_model_fe_abund <- function(FE_formula){
  
  if(is.null(FE_formula)) {
    fml <- as.formula(paste(outcome, "~", covariates))
  }
  else{
    fe_vars <- all.vars(FE_formula)
    fml <- as.formula(paste(outcome, "~", covariates, "|", paste(fe_vars, collapse = " + ")))
  }
  feols(fml, vcov = conley(5), data = abund_tar_panel_select)
  
}

# run model

models_abund_pdsi <- purrr::map(FE_list, run_model_fe_abund) 


# extract coefficients
models_abund_pdsi_coef <- map_dfr(names(models_abund_pdsi), function(name) {
  m <- models_abund_pdsi[[name]]
  broom::tidy(m) %>% 
    filter(term == "pdsi_lag0") %>% 
    mutate(FE = name)
  
})

### plot data
fig_st_441 <- models_abund_pdsi_coef %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS"))) %>% 
ggplot(aes(x = FE, y = estimate)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, color = "#007fff") +
  geom_point(size = 6.5, color = "#007fff") +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate",
       title = "Abundance ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank())

ggsave(fig_st_441, file = here("outputs", "figures", "supplement", "fig_st_441.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")
```

### S4.4.2
Alternative model types
```{r}
# set up dictionary
covariates <- "pdsi_lag0 + temp_lag0 + I(temp_lag0^2)"

FE_list <- list("cluster + month + year" = ~cluster_id + month + year,
                "cluster + month" = ~cluster_id + month,
                "cluster + year" = ~cluster_id + year,
                "cluster" = ~cluster_id,
                "OLS" = NULL)


outcome_list <- list(log_abund = "log(mos_per_trap_night + 1)",
                     fepois = "fepois(mos_per_trap_night)",
                     fenegbin = "fenegbin(mos_per_trap_night)")


run_model_modeltype_abund <- function(model_type, FE_formula) {
  
  if (is.null(FE_formula)) {
    # OLS case (no fixed effects)
    
    if(model_type == "log_abund") {
      feols(as.formula(paste("log(mos_per_trap_night + 1) ~", covariates)),
            vcov = conley(5), data = abund_tar_panel_select)
      
    } else if(model_type == "fepois") {
      fepois(as.formula(paste("mos_per_trap_night ~", covariates)),
             vcov = conley(5), data = abund_tar_panel_select)
      
    } else if(model_type == "fenegbin"){
      fenegbin(as.formula(paste("mos_per_trap_night ~", covariates)),
               vcov = conley(5), data = abund_tar_panel_select)
    }
    
  } else {
    # FE case
    
    fe_vars <- all.vars(FE_formula)
    fe_part <- paste(fe_vars, collapse = " + ")
    
    if(model_type == "log_abund") {
      feols(as.formula(paste("log(mos_per_trap_night + 1) ~", covariates, "|", fe_part)),
            vcov = conley(5), data = abund_tar_panel_select)
      
    } else if(model_type == "fepois") {
      fepois(as.formula(paste("mos_per_trap_night ~", covariates, "|", fe_part)),
             vcov = conley(5), data = abund_tar_panel_select)
      
    } else if(model_type == "fenegbin"){
      fenegbin(as.formula(paste("mos_per_trap_night ~", covariates, "|", fe_part)),
               vcov = conley(5), data = abund_tar_panel_select)
    }
  }
}

# extract coefficients
models_abund_modtype_pdsi_coef <- map_dfr(names(FE_list), function(fe_name) {
  
  FE_formula <- FE_list[[fe_name]]
  
  map_dfr(names(outcome_list), function(model_name){
    m <- run_model_modeltype_abund(model_name, FE_formula)
    
    broom::tidy(m) %>% 
      filter(term == "pdsi_lag0") %>% 
      mutate(FE = fe_name,
             model_type = model_name)
  })
})

## plot
fig_st_442 <- models_abund_modtype_pdsi_coef %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS"))) %>% 
ggplot(aes(x = FE, y = estimate, color = model_type)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("log_abund" = "#016392", #"#016392",
                                "fepois" = "#1F9E89",  #"#C72E29",
                                "fenegbin" = "#D87B82"), #"#098154"),
                     labels = c("log(Abundance+1)", "FE Poisson", "FE NegBin")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "Model Type",
       title = "Abundance ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom") 

ggsave(fig_st_442, file = here("outputs", "figures", "supplement", "fig_st_442.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")
```

### S4.4.3
Alternative PDSI lags
```{r}

pdsi_lags <- c("0-month lag" = "pdsi_lag0",
               "1-month lag" = "pdsi_lag1",
               "2-month lag" = "pdsi_lag2",
               "3-month lag" = "pdsi_lag3",
               "4-month lag" = "pdsi_lag4")

FE_list <- list("cluster + month + year" = ~cluster_id + month + year,
                "cluster + month" = ~cluster_id + month,
                "cluster + year" = ~cluster_id + year,
                "cluster" = ~cluster_id,
                "OLS" = NULL)


run_model_fe_abund_pdsilags <- function(pdsi_var, FE_formula) {
  
  # RHS of regression
  rhs <- paste(pdsi_var, "+ temp_lag0 + I(temp_lag0^2)")
  
  if (is.null(FE_formula)) {
    
    # OLS (no FE)
    fml <- as.formula(paste("log(mos_per_trap_night + 1) ~", rhs))
    
  } else {
    
    # FE case
    fe_part <- paste(all.vars(FE_formula), collapse = " + ")
    fml <- as.formula(paste("log(mos_per_trap_night + 1) ~", rhs, "|", fe_part))
  }
  
  feols(fml, vcov = conley(5), data = abund_tar_panel_select)
}


# run all models + extract coefficients
models_abund_pdsilags_coef <- purrr::map_dfr(names(FE_list), function(fe_name) {
  
  FE_formula <- FE_list[[fe_name]]
  
  purrr::map_dfr(names(pdsi_lags), function(lag_name) {
    
    pdsi_var <- pdsi_lags[[lag_name]]
    
    m <- run_model_fe_abund_pdsilags(pdsi_var, FE_formula)
    
    broom::tidy(m) %>% 
      dplyr::filter(term == pdsi_var) %>% 
      dplyr::mutate(
        FE = fe_name,
        pdsi_lag = lag_name
      )
  })
})


## plot

fig_st_443 <- models_abund_pdsilags_coef %>% 
  filter(pdsi_lag != "4-month lag") %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS"))) %>% 
ggplot(aes(x = FE, y = estimate, color = pdsi_lag)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#016392","#1F9E89",  "#E0AC5F","#D87B82")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "PDSI Lags",
       title = "Abundance ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom") 


ggsave(fig_st_443, file = here("outputs", "figures", "supplement", "fig_st_443.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")

```

### S4.4.4
Alternative temperature functional forms
```{r}
## build model
control_list <- c("no temp" = "pdsi_lag0",
                  "temp linear" = "pdsi_lag0 + temp_lag0",
                  "temp quadratic" = "pdsi_lag0 + temp_lag0 + I(temp_lag0^2)")


run_model_fe_abund_tempform <- function(covariates, FE_formula){
  
  if (is.null(FE_formula)) {
    
    fml <- as.formula(paste(outcome, "~", covariates))
    
  } else {
    
    fe_vars <- all.vars(FE_formula)
    fe_part <- paste(fe_vars, collapse = " + ")
    
    fml <- as.formula(paste(outcome, "~", covariates, "|", fe_part))
  }
  
  feols(fml, vcov = conley(5), data = abund_tar_panel_select)
}

models_abund_tempform_coef <- purrr::map_dfr(names(FE_list), function(fe_name) {
  
  FE_formula <- FE_list[[fe_name]]
  
  purrr::map_dfr(names(control_list), function(control_name) {
    
    covars <- control_list[[control_name]]
    
    m <- run_model_fe_abund_tempform(covars, FE_formula)
    
    broom::tidy(m) %>% 
      dplyr::filter(term == "pdsi_lag0") %>% 
      dplyr::mutate(FE = fe_name,
                    control_spec = control_name)
  })
})

## plot
fig_st_444 <- models_abund_tempform_coef %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS"))) %>% 
ggplot(aes(x = FE, y = estimate, color = control_spec)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#016392","#1F9E89","#D87B82")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "Controls",
       title = "Abundance ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom") 

ggsave(fig_st_444, file = here("outputs", "figures", "supplement", "fig_st_444.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")
```

### S4.4.5
Alternative Conley spatial cutoffs
```{r}

## build model
conley_list <- c("1.5" = 1.5,
                 "5" = 5,
                 "10" = 10,
                 "15" = 15,
                 "20" = 20,
                 "25" = 25)

# formulate model
run_model_fe_conley <- function(FE_formula, conley_cutoff){
  
  covariates <- "pdsi_lag0 + temp_lag0 + I(temp_lag0^2)"
  
  if (is.null(FE_formula)) {
    
    fml <- as.formula(paste(outcome, "~", covariates))
    
  } else {
    
    fe_vars <- all.vars(FE_formula)
    fe_part <- paste(fe_vars, collapse = " + ")
    
    fml <- as.formula(paste(outcome, "~", covariates, "|", fe_part))
  }
  
  feols(fml,
        vcov = conley(conley_cutoff),
        data = abund_tar_panel_select)
}

models_abund_conley_coef <- purrr::map_dfr(names(FE_list), function(fe_name) {
  
  FE_formula <- FE_list[[fe_name]]
  
  purrr::map_dfr(names(conley_list), function(conley_name) {
    
    cutoff <- conley_list[[conley_name]]
    
    m <- run_model_fe_conley(FE_formula, cutoff)
    
    broom::tidy(m) %>% 
      dplyr::filter(term == "pdsi_lag0") %>% 
      dplyr::mutate(FE = fe_name,
                    conley_km = conley_name)
  })
})

## plot it
fig_st_445 <- models_abund_conley_coef  %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS")),
         conley_km = factor(conley_km, levels = c("1.5",
                                                  "5", 
                                                  "10",
                                                  "15",
                                                  "20",
                                                  "25"))) %>% 
ggplot(aes(x = FE, y = estimate, color = conley_km)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#016392","#1F9E89", "#7E8C69", "#E0AC5F","#D87B82", "#B85C38")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "Conley SEs",
       title = "Abundance ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom")  +
  guides(color = guide_legend(nrow = 1))

ggsave(fig_st_445, file = here("outputs", "figures", "supplement", "fig_st_445.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")

```

### S4.5
Supporting figures - histogram
```{r}

raw <- abund_tar_panel_select %>% 
  ggplot(aes(x = mos_per_trap_night)) +
  geom_histogram(fill = "#007fff", color = "#606372") + #"#79A8A4"
  labs(x = "Number of trap stations per cluster", y = "Count of clusters") +
  ggtitle("Raw Distribution") +
  theme(axis.title = element_text(size = 14, face = "bold")) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Count") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.position = "none") 


log <- abund_tar_panel_select %>% 
  ggplot(aes(x = log(mos_per_trap_night+1))) +
  geom_histogram(fill = "#007fff", color = "#606372") + #"#79A8A4"
  labs(x = "Number of trap stations per cluster", y = "Count of clusters") +
  ggtitle("Log-transformed Distribution") +
  theme(axis.title = element_text(size = 14, face = "bold")) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Count") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.position = "none") 

## combine both
hist_both <- ggarrange(raw + rremove("xlab"), log + rremove("ylab") + rremove("xlab"), common.legend = TRUE)

hist_both_an <- annotate_figure(hist_both, 
                                bottom = text_grob("Mean Mosquitoes per Trap Night", size = 18, face = "bold"))

ggsave(hist_both_an, file = here("outputs", "figures", "supplement", "fig_st_45_hist.png"), 
        height = 5, width = 12,
       dpi = 400, bg = "white")
```

Supporting figures - marginal effects plots
```{r}
######## PDSI
# Create grid of PDSI values
pdsi_seq <- seq(min(abund_tar_panel_select$pdsi_lag0, na.rm = TRUE), 
                max(abund_tar_panel_select$pdsi_lag0, na.rm = TRUE), 
                length.out = 100)

# Mean temperature for holding constant
mean_temp <- mean(abund_tar_panel_select$temp_lag0, na.rm = TRUE)

# Use predict from fixest with se.fit = TRUE
pred <- predict(mod_fe_abund_pdsi_csw[[1]], 
                newdata = data.frame(pdsi_lag0 = pdsi_seq,
                                     temp_lag0 = mean_temp),
                se.fit = TRUE, type = "response") 

# Build dataframe for plotting
plot_df <- data.frame(pdsi = pdsi_seq, fit = pred$fit,
                      lower = pred$fit - 1.96 * pred$se.fit, upper = pred$fit + 1.96 * pred$se.fit)

# Plot predicted effect
mod_ols_abund_pdsi_ME <- ggplot(plot_df, aes(x = pdsi, y = fit)) +
  geom_line(size = 1.3, color = "#007fff") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#007fff") +
  labs(x = "Palmer Drought Severity Index (PDSI)", 
       y = "Predicted log(mosquitoes per trap night + 1)") +
  theme_minimal(base_size = 13) +
  theme_classic() +
  scale_x_continuous(expand = c(0,0)) +
  theme(axis.title = element_text(face = "bold", size = 13),
        axis.text = element_text(size = 12))

######## TEMP^2
# Create grid of TEMP^2 values
temp_seq <- seq(min(abund_tar_panel_select$temp_lag0, na.rm = TRUE), 
                max(abund_tar_panel_select$temp_lag0, na.rm = TRUE), 
                length.out = 100)

temp_raw_seq <- seq(min(abund_tar_panel_select$temp_raw, na.rm = TRUE), 
                max(abund_tar_panel_select$temp_raw, na.rm = TRUE), 
                length.out = 100)

# Mean pdsi for holding constant
mean_pdsi <- mean(abund_tar_panel_select$pdsi_lag0, na.rm = TRUE)

# Use predict from fixest with se.fit = TRUE
pred <- predict(mod_fe_abund_pdsi_csw[[1]], 
                newdata = data.frame(pdsi_lag0 = mean_pdsi,
                                     temp_lag0 = temp_seq),
                se.fit = TRUE, type = "response") 

# Build dataframe for plotting
plot_df <- data.frame(temp_C = temp_raw_seq, fit = pred$fit,
                      lower = pred$fit - 1.96 * pred$se.fit, upper = pred$fit + 1.96 * pred$se.fit)


mod_ols_abund_temp_ME <- ggplot(plot_df, aes(x = temp_C, y = fit)) +
  geom_line(size = 1.3, color = "#007fff") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#007fff") +
  labs(x = "Temperature (°C)", 
       y = "Predicted Abundance") +
  theme_minimal(base_size = 13) +
  theme_classic() +
  scale_x_continuous(expand = c(0,0)) +
  theme(axis.title = element_text(face = "bold", size = 13),
        axis.text = element_text(size = 12))

ggsave(mod_ols_abund_temp_ME, file = here("outputs", "figures", "supplement", "fig_st_45_METemp.png"), 
       height = 3, width = 4,
       dpi = 400, bg = "white")
```





## WNV MIR
## Text S5

### S5.1-S5.2
```{r}
## build model 
mod_fe_wnv_pdsi <- feols(log(WNV_MIR + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = wnv_tar_panel_under101)

# check summaries
summary(mod_fe_wnv_pdsi)
round(confint(mod_fe_wnv_pdsi, level = 0.95),2)

# clean up
broom::tidy(mod_fe_wnv_pdsi) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))
```

### S5.3.1
Tale of varying fixed effects
```{r}

mod_fe_wnv_pdsi_csw <- feols(log(WNV_MIR + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             csw0(cluster_id, cluster_id + year, cluster_id + month, cluster_id + year + month),
                           vcov = conley(5),
                           data = wnv_tar_panel_under101)

etable(mod_fe_wnv_pdsi_csw,
       headers = c("OLS", "Cluster FE", "Cluster + Month FE",
                   "Cluster + Year FE", "Cluster + Month + Year FE"),
       dict = c("log(WNV_MIR +1)" = "WNV MIR",
                pdsi_lag0 = "PDSI",
                temp_lag0 = "Temp (std)",
                temp_lag0_sq = "Temp^2 (std)"),
       fitstat = ~ n + r2 + wr2,
        digits = 3, style.tex = style.tex("aer"))



```

### S5.3.2
Multicollinearity
```{r}
mod_ols_wnv_pdsi <- lm(log(WNV_MIR + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0, data = wnv_tar_panel_under101)
vif(mod_ols_wnv_pdsi)
```

(Robustness checks)
### S5.4.1 
Alternative fixed effects
```{r}
### format data
# set up dictionary
outcome <- "log(WNV_MIR + 1)"

covariates <- "pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0"

FE_list <- list("cluster + month + year" = ~cluster_id + month + year,
                "cluster + month" = ~cluster_id + month,
                "cluster + year" = ~cluster_id + year,
                "cluster" = ~cluster_id,
                "OLS" = NULL)


run_model_fe_wnv <- function(FE_formula){
  
  if(is.null(FE_formula)) {
    fml <- as.formula(paste(outcome, "~", covariates))
  }
  else{
    fe_vars <- all.vars(FE_formula)
    fml <- as.formula(paste(outcome, "~", covariates, "|", paste(fe_vars, collapse = " + ")))
  }
  feols(fml, vcov = conley(5), data = wnv_tar_panel_under101)
  
}

# run model

models_wnv_pdsi <- purrr::map(FE_list, run_model_fe_wnv) 


# extract coefficients
models_wnv_pdsi_coef <- map_dfr(names(models_wnv_pdsi), function(name) {
  m <- models_wnv_pdsi[[name]]
  broom::tidy(m) %>% 
    filter(term == "pdsi_lag0") %>% 
    mutate(FE = name)
  
})

### plot data
fig_st_541 <- models_wnv_pdsi_coef %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS"))) %>% 
ggplot(aes(x = FE, y = estimate)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, color = "#007fff") +
  geom_point(size = 6.5, color = "#007fff") +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate",
       title = "WNV MIR ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank())

ggsave(fig_st_541, file = here("outputs", "figures", "supplement", "fig_st_541.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")
```

### S5.4.2
Alternative model types
```{r}
# set up dictionary
covariates <- "pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0"

FE_list <- list("cluster + month + year" = ~cluster_id + month + year,
                "cluster + month" = ~cluster_id + month,
                "cluster + year" = ~cluster_id + year,
                "cluster" = ~cluster_id,
                "OLS" = NULL)


outcome_list <- list(log_wnv = "log(WNV_MIR + 1)",
                     fepois = "fepois(WNV_MIR)",
                     fenegbin = "fenegbin(WNV_MIR)")


run_model_modeltype_wnv <- function(model_type, FE_formula) {
  
  if (is.null(FE_formula)) {
    # OLS case (no fixed effects)
    
    if(model_type == "log_wnv") {
      feols(as.formula(paste("log(WNV_MIR + 1) ~", covariates)),
            vcov = conley(5), data = wnv_tar_panel_under101)
      
    } else if(model_type == "fepois") {
      fepois(as.formula(paste("WNV_MIR ~", covariates)),
             vcov = conley(5), data = wnv_tar_panel_under101)
      
    } else if(model_type == "fenegbin"){
      fenegbin(as.formula(paste("WNV_MIR ~", covariates)),
               vcov = conley(5), data = wnv_tar_panel_under101)
    }
    
  } else {
    # FE case
    
    fe_vars <- all.vars(FE_formula)
    fe_part <- paste(fe_vars, collapse = " + ")
    
    if(model_type == "log_wnv") {
      feols(as.formula(paste("log(WNV_MIR + 1) ~", covariates, "|", fe_part)),
            vcov = conley(5), data = wnv_tar_panel_under101)
      
    } else if(model_type == "fepois") {
      fepois(as.formula(paste("WNV_MIR ~", covariates, "|", fe_part)),
             vcov = conley(5), data = wnv_tar_panel_under101)
      
    } else if(model_type == "fenegbin"){
      fenegbin(as.formula(paste("WNV_MIR ~", covariates, "|", fe_part)),
               vcov = conley(5), data = wnv_tar_panel_under101)
    }
  }
}

# extract coefficients
models_wnv_modtype_pdsi_coef <- map_dfr(names(FE_list), function(fe_name) {
  
  FE_formula <- FE_list[[fe_name]]
  
  map_dfr(names(outcome_list), function(model_name){
    m <- run_model_modeltype_wnv(model_name, FE_formula)
    
    broom::tidy(m) %>% 
      filter(term == "pdsi_lag0") %>% 
      mutate(FE = fe_name,
             model_type = model_name)
  })
})

## plot
fig_st_542 <- models_wnv_modtype_pdsi_coef %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS"))) %>% 
ggplot(aes(x = FE, y = estimate, color = model_type)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("log_wnv" = "#016392", #"#016392",
                                "fepois" = "#1F9E89",  #"#C72E29",
                                "fenegbin" = "#D87B82"), #"#098154"),
                     labels = c("log(WNV MIR+1)", "FE Poisson", "FE NegBin")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "Model Type",
       title = "WNV MIR ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom") 

ggsave(fig_st_542, file = here("outputs", "figures", "supplement", "fig_st_542.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")
```

### S5.4.3
Alternative PDSI lags
```{r}

# set up lags
pdsi_lags <- c("0-month lag" = "pdsi_lag0",
               "1-month lag" = "pdsi_lag1",
               "2-month lag" = "pdsi_lag2",
               "3-month lag" = "pdsi_lag3",
               "4-month lag" = "pdsi_lag4")

FE_list <- list("cluster + month + year" = ~cluster_id + month + year,
                "cluster + month" = ~cluster_id + month,
                "cluster + year" = ~cluster_id + year,
                "cluster" = ~cluster_id,
                "OLS" = NULL)


run_model_fe_wnv_pdsilags <- function(pdsi_var, FE_formula) {
  
  # RHS of regression
  rhs <- paste(pdsi_var, "+ temp_lag0 + I(temp_lag0^2) + bird_lag0")
  
  if (is.null(FE_formula)) {
    
    # OLS (no FE)
    fml <- as.formula(paste("log(WNV_MIR + 1) ~", rhs))
    
  } else {
    
    # FE case
    fe_part <- paste(all.vars(FE_formula), collapse = " + ")
    fml <- as.formula(paste("log(WNV_MIR+ 1) ~", rhs, "|", fe_part))
  }
  
  feols(fml, vcov = conley(5), data = wnv_tar_panel_under101)
}


# run all models + extract coefficients
models_wnv_pdsilags_coef <- purrr::map_dfr(names(FE_list), function(fe_name) {
  
  FE_formula <- FE_list[[fe_name]]
  
  purrr::map_dfr(names(pdsi_lags), function(lag_name) {
    
    pdsi_var <- pdsi_lags[[lag_name]]
    
    m <- run_model_fe_wnv_pdsilags(pdsi_var, FE_formula)
    
    broom::tidy(m) %>% 
      dplyr::filter(term == pdsi_var) %>% 
      dplyr::mutate(
        FE = fe_name,
        pdsi_lag = lag_name)
  })
})


## plot

fig_st_543 <- models_wnv_pdsilags_coef %>% 
  filter(pdsi_lag != "4-month lag") %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS"))) %>% 
ggplot(aes(x = FE, y = estimate, color = pdsi_lag)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#016392","#1F9E89",  "#E0AC5F","#D87B82")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "PDSI Lags",
       title = "WNV MIR ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom") 


ggsave(fig_st_543, file = here("outputs", "figures", "supplement", "fig_st_543.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")

```

### S5.4.4
Alternative temperature functional forms
```{r}
outcome <- "log(WNV_MIR + 1)"

## build model
control_list <- c("no temp" = "pdsi_lag0 + bird_lag0",
                  "temp linear" = "pdsi_lag0 + temp_lag0 + bird_lag0",
                  "temp quadratic" = "pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0")


run_model_fe_wnv_tempform <- function(covariates, FE_formula){
  
  if (is.null(FE_formula)) {
    
    fml <- as.formula(paste(outcome, "~", covariates))
    
  } else {
    
    fe_vars <- all.vars(FE_formula)
    fe_part <- paste(fe_vars, collapse = " + ")
    
    fml <- as.formula(paste(outcome, "~", covariates, "|", fe_part))
  }
  
  feols(fml, vcov = conley(5), data = wnv_tar_panel_under101)
}

models_wnv_tempform_coef <- purrr::map_dfr(names(FE_list), function(fe_name) {
  
  FE_formula <- FE_list[[fe_name]]
  
  purrr::map_dfr(names(control_list), function(control_name) {
    
    covars <- control_list[[control_name]]
    
    m <- run_model_fe_wnv_tempform(covars, FE_formula)
    
    broom::tidy(m) %>% 
      dplyr::filter(term == "pdsi_lag0") %>% 
      dplyr::mutate(FE = fe_name,
                    control_spec = control_name)
  })
})

## plot
fig_st_544 <- models_wnv_tempform_coef %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS"))) %>% 
ggplot(aes(x = FE, y = estimate, color = control_spec)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#016392","#1F9E89","#D87B82")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "Controls",
       title = "WNV MIR ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom") 

ggsave(fig_st_544, file = here("outputs", "figures", "supplement", "fig_st_544.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")
```

### S5.4.5
Alternative Conley spatial cutoffs
```{r}
outcome <- "log(WNV_MIR + 1)"
## build model
conley_list <- c("1.5" = 1.5,
                 "5" = 5,
                 "10" = 10,
                 "15" = 15,
                 "20" = 20,
                 "25" = 25)

# formulate model
run_model_fe_conley <- function(FE_formula, conley_cutoff){
  
  covariates <- "pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0"
  
  if (is.null(FE_formula)) {
    
    fml <- as.formula(paste(outcome, "~", covariates))
    
  } else {
    
    fe_vars <- all.vars(FE_formula)
    fe_part <- paste(fe_vars, collapse = " + ")
    
    fml <- as.formula(paste(outcome, "~", covariates, "|", fe_part))
  }
  
  feols(fml,
        vcov = conley(conley_cutoff),
        data = wnv_tar_panel_under101)
}

models_wnv_conley_coef <- purrr::map_dfr(names(FE_list), function(fe_name) {
  
  FE_formula <- FE_list[[fe_name]]
  
  purrr::map_dfr(names(conley_list), function(conley_name) {
    
    cutoff <- conley_list[[conley_name]]
    
    m <- run_model_fe_conley(FE_formula, cutoff)
    
    broom::tidy(m) %>% 
      dplyr::filter(term == "pdsi_lag0") %>% 
      dplyr::mutate(FE = fe_name,
                    conley_km = conley_name)
  })
})

## plot it
fig_st_545 <- models_wnv_conley_coef  %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS")),
         conley_km = factor(conley_km, levels = c("1.5",
                                                  "5", 
                                                  "10",
                                                  "15",
                                                  "20",
                                                  "25"))) %>% 
ggplot(aes(x = FE, y = estimate, color = conley_km)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#016392","#1F9E89", "#7E8C69", "#E0AC5F","#D87B82", "#B85C38")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "Conley SEs",
       title = "WNV MIR ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom")  +
  guides(color = guide_legend(nrow = 1))

ggsave(fig_st_545, file = here("outputs", "figures", "supplement", "fig_st_545.png"), 
       height = 5, width = 12.2,
       dpi = 400, bg = "white")

```

### S5.4.6
WNV MIR cutoffs
```{r}
outcome <- "log(WNV_MIR + 1)"
covariates <- "pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0"

data_list <- list(
  full = (wnv_tar_panel_select %>% filter(WNV_MIR <= 1000)), 
  under1000 = (wnv_tar_panel_select %>% filter(WNV_MIR < 1000)),
  under101 = (wnv_tar_panel_select %>% filter(WNV_MIR <= 100)),
  capped100 = wnv_tar_panel_select %>% mutate(WNV_MIR = pmin(WNV_MIR, 100)))


run_model_modeltype_wnv <- function(model_type, FE_formula, data) {
  
  if (is.null(FE_formula)) {
    
    if(model_type == "log_wnv") {
      feols(as.formula(paste("log(WNV_MIR + 1) ~", covariates)),
            vcov = conley(5), data = data)
      
    } else if(model_type == "fepois") {
      fepois(as.formula(paste("WNV_MIR ~", covariates)),
             vcov = conley(5), data = data)
      
    } else if(model_type == "fenegbin"){
      fenegbin(as.formula(paste("WNV_MIR ~", covariates)),
               vcov = conley(5), data = data)
    }
    
  } else {
    
    fe_vars <- all.vars(FE_formula)
    fe_part <- paste(fe_vars, collapse = " + ")
    
    if(model_type == "log_wnv") {
      feols(as.formula(paste("log(WNV_MIR + 1) ~", covariates, "|", fe_part)),
            vcov = conley(5), data = data)
      
    } else if(model_type == "fepois") {
      fepois(as.formula(paste("WNV_MIR ~", covariates, "|", fe_part)),
             vcov = conley(5), data = data)
      
    } else if(model_type == "fenegbin"){
      fenegbin(as.formula(paste("WNV_MIR ~", covariates, "|", fe_part)),
               vcov = conley(5), data = data)
    }
  }
}

results <- map_dfr(names(data_list), function(data_name) {
  
  data <- data_list[[data_name]]
  
  map_dfr(names(FE_list), function(fe_name) {
    
    FE_formula <- FE_list[[fe_name]]
    
    map_dfr(names(outcome_list), function(model_name) {
      
      m <- run_model_modeltype_wnv(model_name, FE_formula, data)
      
      broom::tidy(m) %>%
        filter(term == "pdsi_lag0") %>%
        mutate(FE = fe_name,
               model_type = model_name,
               sample = data_name)
    })
  })
})


## plot
fig_st_546 <- results %>% 
  mutate(FE = factor(FE, levels = c("cluster + month + year",
                                    "cluster + year",
                                    "cluster + month",
                                    "cluster",
                                    "OLS")),
        sample = factor(sample, levels = c("full", 
                                           "under1000",
                                           "under101", 
                                           "capped100"),
                        labels = c("≤ 1000",
                                   "< 1000", 
                                   "≤ 100",
                                   "cap at 100"))) %>% 
ggplot(aes(x = sample, y = estimate, color = model_type)) +
  geom_errorbar(aes(ymin = estimate - 1.96*std.error,
                    ymax =  estimate + 1.96*std.error), width = .15, linewidth = 2, 
                position = position_dodge(width = .6)) +
  geom_point(size = 6.5, position = position_dodge(width = .6)) +
  geom_hline(yintercept = 0, linetype = "dashed",linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("log_wnv" = "#016392", #"#016392",
                                "fepois" = "#1F9E89",  #"#C72E29",
                                "fenegbin" = "#D87B82"), #"#098154"),
                     labels = c("log(WNV MIR+1)", "FE Poisson", "FE NegBin")) +
  theme_minimal(base_size = 18) + 
  labs(x = "Fixed Effects", y = "Coefficient Estimate", color = "Model Type",
       title = "WNV MIR ~ PDSI + Controls + FE") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(size = 19),
        axis.text.y = element_text(size = 19),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 16),
        legend.position = "bottom") +
  facet_wrap(~FE, nrow = 3)

ggsave(fig_st_546, file = here("outputs", "figures", "supplement", "fig_st_546.png"), 
       height = 7, width = 12.2,
       dpi = 400, bg = "white")


```

### S4.5
Supporting figures - histogram
```{r}
### WITH ZERO
raw_wnv <- wnv_tar_panel_under101 %>% 
  ggplot(aes(x = WNV_MIR)) +
  geom_histogram(fill = "#007fff", color = "#606372") + #"#79A8A4"
  labs(x = "Number of trap stations per cluster", y = "Count of clusters") +
  ggtitle("Raw Distribution") +
  theme(axis.title = element_text(size = 14, face = "bold")) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Count") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.position = "none") 


log_wnv <- wnv_tar_panel_under101 %>% 
  ggplot(aes(x = log(WNV_MIR+1))) +
  geom_histogram(fill = "#007fff", color = "#606372") + #"#79A8A4"
  labs(x = "Number of trap stations per cluster", y = "Count of clusters") +
  ggtitle("Log-transformed Distribution") +
  theme(axis.title = element_text(size = 14, face = "bold")) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Count") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.position = "none") 

## combine both
hist_both_wnv <- ggarrange(raw_wnv + rremove("xlab"), log_wnv + rremove("ylab") + rremove("xlab"), common.legend = TRUE)

hist_both_an_wnv <- annotate_figure(hist_both_wnv, 
                                bottom = text_grob("WNV Minimum Infection Rate", size = 18, face = "bold"))



### WITHOUT ZERO
raw_wnv_no0 <- wnv_tar_panel_under101 %>% 
  filter(WNV_MIR != 0) %>% 
  ggplot(aes(x = WNV_MIR)) +
  geom_histogram(fill = "#007fff", color = "#606372") + #"#79A8A4"
  labs(x = "Number of trap stations per cluster", y = "Count of clusters",subtitle = "Non-Zero observations") +
  ggtitle("Raw Distribution") +
  theme(axis.title = element_text(size = 14, face = "bold")) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Count") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.position = "none") 


log_wnv_no0 <- wnv_tar_panel_under101 %>%
  filter(WNV_MIR != 0) %>% 
  ggplot(aes(x = log(WNV_MIR+1))) +
  geom_histogram(fill = "#007fff", color = "#606372") + #"#79A8A4"
  labs(x = "Number of trap stations per cluster", y = "Count of clusters",subtitle = "Non-Zero observations") +
  ggtitle("Log-transformed Distribution") +
  theme(axis.title = element_text(size = 14, face = "bold")) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Count") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.position = "none") 

## combine both
hist_both_wnv_no0 <- ggarrange(raw_wnv_no0 + rremove("xlab"), log_wnv_no0 + rremove("ylab") + rremove("xlab"), common.legend = TRUE)

hist_both_an_wnv_no0 <- annotate_figure(hist_both_wnv_no0, 
                                bottom = text_grob("WNV Minimum Infection Rate", size = 18, face = "bold"))


hist_both_an_wnv_0no0 <- (hist_both_an_wnv/hist_both_an_wnv_no0)
ggsave(hist_both_an_wnv_0no0, file = here("outputs", "figures", "supplement", "fig_st_55_hist.png"), 
        height = 8, width = 12,
       dpi = 400, bg = "white")
```

Supporting figures - marginal effects plots
```{r}
######## PDSI
# Create grid of PDSI values
pdsi_seq <- seq(min(wnv_tar_panel_under101$pdsi_lag0, na.rm = TRUE), 
                max(wnv_tar_panel_under101$pdsi_lag0, na.rm = TRUE), 
                length.out = 100)

# Mean temperature for holding constant
mean_temp <- mean(wnv_tar_panel_under101$temp_lag0, na.rm = TRUE)
mean_bird <- mean(wnv_tar_panel_under101$bird_lag0, na.rm = TRUE)

# Use predict from fixest with se.fit = TRUE
pred <- predict(mod_fe_wnv_pdsi_csw[[1]], 
                newdata = data.frame(pdsi_lag0 = pdsi_seq,
                                     temp_lag0 = mean_temp,
                                     bird_lag0 = mean_bird),
                se.fit = TRUE, type = "response") 

# Build dataframe for plotting
plot_df <- data.frame(pdsi = pdsi_seq, fit = pred$fit,
                      lower = pred$fit - 1.96 * pred$se.fit, upper = pred$fit + 1.96 * pred$se.fit)

# Plot predicted effect
mod_ols_wnv_pdsi_ME <- ggplot(plot_df, aes(x = pdsi, y = fit)) +
  geom_line(size = 1.3, color = "#007fff") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#007fff") +
  labs(x = "Palmer Drought Severity Index (PDSI)", 
       y = "Predicted log(WNV MIR + 1)") +
  theme_minimal(base_size = 13) +
  theme_classic() +
  scale_x_continuous(expand = c(0,0)) +
  theme(axis.title = element_text(face = "bold", size = 13),
        axis.text = element_text(size = 12))

######## TEMP^2
# Create grid of TEMP^2 values
temp_seq <- seq(min(wnv_tar_panel_under101$temp_lag0, na.rm = TRUE), 
                max(wnv_tar_panel_under101$temp_lag0, na.rm = TRUE), 
                length.out = 100)

temp_raw_seq <- seq(min(wnv_tar_panel_under101$temp_raw, na.rm = TRUE), 
                max(wnv_tar_panel_under101$temp_raw, na.rm = TRUE), 
                length.out = 100)

# Mean pdsi for holding constant
mean_pdsi <- mean(wnv_tar_panel_under101$pdsi_lag0, na.rm = TRUE)
mean_bird <- mean(wnv_tar_panel_under101$bird_lag0, na.rm = TRUE)

# Use predict from fixest with se.fit = TRUE
pred <- predict(mod_fe_wnv_pdsi_csw[[1]], 
                newdata = data.frame(pdsi_lag0 = mean_pdsi,
                                     temp_lag0 = temp_seq,
                                     bird_lag0 = mean_bird),
                se.fit = TRUE, type = "response") 

# Build dataframe for plotting
plot_df <- data.frame(temp_C = temp_raw_seq, fit = pred$fit,
                      lower = pred$fit - 1.96 * pred$se.fit, upper = pred$fit + 1.96 * pred$se.fit)


mod_ols_wnv_temp_ME <- ggplot(plot_df, aes(x = temp_C, y = fit)) +
  geom_line(size = 1.3, color = "#007fff") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#007fff") +
  labs(x = "Temperature (°C)", 
       y = "Predicted WNV MIR") +
  theme_minimal(base_size = 13) +
  theme_classic() +
  scale_x_continuous(expand = c(0,0)) +
  theme(axis.title = element_text(face = "bold", size = 13),
        axis.text = element_text(size = 12))

ggsave(mod_ols_wnv_temp_ME, file = here("outputs", "figures", "supplement", "fig_st_55_METemp.png"), 
       height = 3, width = 4,
       dpi = 400, bg = "white")



######## Bird INDEX
######## BIRD marginal effect plot

# Create grid of standardized bird values
bird_seq <- seq(
  min(wnv_tar_panel_under101$bird_lag0, na.rm = TRUE), 
  max(wnv_tar_panel_under101$bird_lag0, na.rm = TRUE), 
  length.out = 100
)

# Matching raw bird composition values for plotting
bird_raw_seq <- seq(
  min(wnv_tar_panel_under101$bird_raw, na.rm = TRUE), 
  max(wnv_tar_panel_under101$bird_raw, na.rm = TRUE), 
  length.out = 100
)

# Hold other covariates constant
mean_pdsi <- mean(wnv_tar_panel_under101$pdsi_lag0, na.rm = TRUE)
mean_temp <- mean(wnv_tar_panel_under101$temp_lag0, na.rm = TRUE)

# Predictions
pred <- predict(
  mod_fe_wnv_pdsi_csw[[1]], 
  newdata = data.frame(
    pdsi_lag0 = mean_pdsi,
    temp_lag0 = mean_temp,
    bird_lag0 = bird_seq
  ),
  se.fit = TRUE,
  type = "response"
)

# Build dataframe
plot_df <- data.frame(
  bird_raw = bird_raw_seq,
  fit = pred$fit,
  lower = pred$fit - 1.96 * pred$se.fit,
  upper = pred$fit + 1.96 * pred$se.fit)


# Plot
mod_ols_wnv_bird_ME <- ggplot(plot_df, aes(x = bird_raw, y = fit)) +
  geom_line(size = 1.3, color = "#007fff") +
  geom_ribbon(aes(ymin = lower, ymax = upper),
              alpha = 0.2,
              fill = "#007fff") +
  labs(x = "Bird Community Competence",  y = "Predicted WNV MIR") +
  theme_minimal(base_size = 13) +
  theme_classic() +
  scale_x_continuous(expand = c(0,0)) +
  theme(
    axis.title = element_text(face = "bold", size = 13),
    axis.text = element_text(size = 12))

ggsave(mod_ols_wnv_bird_ME, file = here("outputs", "figures", "supplement", "fig_st_55_MEBird.png"), 
       height = 3, width = 4,
       dpi = 400, bg = "white")


fig_st_55_ME_both <- (mod_ols_wnv_temp_ME + mod_ols_wnv_bird_ME)

ggsave(fig_st_55_ME_both, file = here("outputs", "figures", "supplement", "fig_st_55_MEboth.png"), 
       height = 3, width = 8,
       dpi = 400, bg = "white")
```


# Spatial Heterogeneity of PDSI

## Text S6

### Abundance
### S6.1
Model summary
```{r}
# build model
mod_fe_abund_pdsi_HR <- feols(log(mos_per_trap_night + 1) ~ i(hydro_region, pdsi_lag0) + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_select)

# check summary
summary(mod_fe_abund_pdsi_HR)
confint(mod_fe_abund_pdsi_HR, level = 0.95)

# look at table
etable(mod_fe_abund_pdsi_HR)


# clean up
broom::tidy(mod_fe_abund_pdsi_HR) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))
```

Plot county level effects
```{r}
# build model
mod_fe_abund_pdsi_county <- feols(log(mos_per_trap_night + 1) ~ i(county, pdsi_lag0) + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_select)


## make tidy
abund_pdsi_county_coef <- broom::tidy(mod_fe_abund_pdsi_county) %>% 
  filter(grepl("county::", term)) %>% 
  mutate(county = gsub("county::", "", term),
         county = gsub(":pdsi_lag0", "", county),
         lower = estimate - 1.96 * std.error,
         upper = estimate + 1.96 * std.error) %>% 
  left_join(county_to_hr, by = "county")

## plot
fig_st_61 <- abund_pdsi_county_coef %>% 
  mutate(county = reorder(county, -estimate)) %>% 
  ggplot(aes(x = county, y = estimate, color = hydro_region)) +
  geom_errorbar(aes(ymin = estimate - 1.96 * std.error,
                    ymax = estimate + 1.96 * std.error),width = 0.35, linewidth = 2,
                position = position_dodge(width = 0.65)) +
  geom_point(size = 6.5,position = position_dodge(width = 0.65)) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005" )) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Effect of PDSI", color = "Hydrological Region") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.title = element_text(face = "bold"),
    legend.position = "right") +
  coord_flip() +
  ggtitle("Abundance")


ggsave(fig_st_61, file = here("outputs", "figures", "supplement", "fig_st_61.png"), 
       height = 7, width = 10,
       dpi = 400, bg = "white")
```


### WNV MIR
### S6.2
Model summary
```{r}
# build model
mod_fe_wnv_pdsi_HR <- feols(log(WNV_MIR + 1) ~ i(hydro_region, pdsi_lag0) + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = wnv_tar_panel_under101)

# check summary
summary(mod_fe_wnv_pdsi_HR)
confint(mod_fe_wnv_pdsi_HR, level = 0.95)

# look at table
etable(mod_fe_wnv_pdsi_HR)


# clean up
broom::tidy(mod_fe_wnv_pdsi_HR) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))
```

Plot county level effects
```{r}
# build model
mod_fe_wnv_pdsi_county <- feols(log(WNV_MIR + 1) ~ i(county, pdsi_lag0) + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = wnv_tar_panel_under101)


## make tidy
wnv_pdsi_county_coef <- broom::tidy(mod_fe_wnv_pdsi_county) %>% 
  filter(grepl("county::", term)) %>% 
  mutate(county = gsub("county::", "", term),
         county = gsub(":pdsi_lag0", "", county),
         lower = estimate - 1.96 * std.error,
         upper = estimate + 1.96 * std.error) %>% 
  left_join(county_to_hr, by = "county")

## plot
fig_st_62 <- wnv_pdsi_county_coef %>% 
  mutate(county = reorder(county, -estimate)) %>% 
  ggplot(aes(x = county, y = estimate, color = hydro_region)) +
  geom_errorbar(aes(ymin = estimate - 1.96 * std.error,
                    ymax = estimate + 1.96 * std.error),width = 0.35, linewidth = 2,
                position = position_dodge(width = 0.65)) +
  geom_point(size = 6.5,position = position_dodge(width = 0.65)) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 1, color = "grey10") +
  scale_color_manual(values = c("#ADC397","#DFBF2B","#EA8005" )) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Effect of PDSI", color = "Hydrological Region") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.title = element_text(face = "bold"),
    legend.position = "right") +
  coord_flip() +
  ggtitle("WNV MIR")


ggsave(fig_st_62, file = here("outputs", "figures", "supplement", "fig_st_62.png"), 
       height = 7, width = 10,
       dpi = 400, bg = "white")
```

## S7.1
Abundance ~ HVs
```{r}

both_hydro_coef <- read.csv(here("outputs", "models", "both_hydro_coef.csv"))


both_hydro_coef %>% 
  filter(outcome == "Abundance") %>% 
  #filter(lag == "3 mo") %>% 
  mutate(sig = case_when(p.value < 0.001 ~ "***",
                         p.value < 0.01  ~ "**",
                         p.value < 0.05  ~ "*",TRUE ~ "")) %>% 
  dplyr::select(hydro_var, lag, estimate, std.error,sig) %>% 
  mutate(across(where(is.numeric), ~ round(., 3)))


```

## S8.1
WNV MIR ~ HVs
```{r}

#both_hydro_coef <- read.csv(here("outputs", "models", "both_hydro_coef.csv"))


both_hydro_coef %>% 
  filter(outcome == "WNV MIR") %>% 
  #filter(lag == "3 mo") %>% 
  mutate(sig = case_when(p.value < 0.001 ~ "***",
                         p.value < 0.01  ~ "**",
                         p.value < 0.05  ~ "*",TRUE ~ "")) %>% 
  dplyr::select(hydro_var, lag, estimate, std.error,sig) %>% 
  mutate(across(where(is.numeric), ~ round(., 3)))

## plot 5 vs 10 km buffer
hydro_colors <- c(  
  "Soil Moisture" =     "#D3105C" , 
  "Evapotranspiration" = "#3A5D3D",
  "Standing Water" =  "#4C4976",
  "Standing Water (10km)" = "#D87B82")

lag_alpha <- c("0 mo" = 1,
               "1 mo" = 0.75,
               "2 mo" = 0.55,
               "3 mo" = 0.35)

fig_st_72 <- 
  both_hydro_coef %>% 
  filter(hydro_var == "Standing Water (10km)" |
           hydro_var == "Standing Water") %>% 
  ggplot(aes(x = outcome, y = estimate, color = hydro_var, alpha = lag)) +
  geom_errorbar(aes(ymin = estimate - 1.96 * std.error,
                    ymax = estimate + 1.96 * std.error),width = 0.35, linewidth = 2,
                position = position_dodge(width = 0.65)) +
  geom_point(size = 4.5,position = position_dodge(width = 0.65)) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 1, color = "grey10") +
  scale_color_manual(values = c(hydro_colors)) +
  scale_alpha_manual(values = lag_alpha) +
  theme_minimal(base_size = 18) +
  labs(x = "",y = "Coefficient Estimate", alpha = "Month Lag") +
  theme(axis.title = element_text(face = "bold"),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18),
    panel.grid.minor = element_blank(),
    legend.title = element_text(face = "bold"),
    legend.position = "bottom",
    strip.text = element_text(face = "bold", size = 20)) +
  facet_wrap(~hydro_var, ncol = 2) +
  guides(color = FALSE) 


ggsave(fig_st_72, file = here("outputs", "figures", "supplement", "fig_st_72.png"), 
       height = 4, width = 8,
       dpi = 400, bg = "white")
```


(sensitivity checks)

## S8.1.2
Alternative vector species

### Abundance
format data
```{r}

## already have
# abund_tar_panel_select. 

## upload covariate data
station_covariates_full <- read.csv(here("data" ,"interim", "covariates_scalelag_stationmeta.csv"))

station_covariates_filtered <- station_covariates_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month)) 


### PIP
## upload culex pipiens data
abund_pip_panel_full <- read.csv(here("data", "interim", "abundance_pip_cluster.csv"))


abund_pip_panel_filtered <- abund_pip_panel_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  dplyr::rename(year = surv_year) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month))

## combine
abund_pip_panel_select <- abund_pip_panel_filtered %>% 
  left_join(station_covariates_filtered %>% dplyr::select(-county), by = c("cluster_id", "year", "month"))


### QUINQ
## upload culex quinq data
abund_quin_panel_full <- read.csv(here("data", "interim", "abundance_quin_cluster.csv"))

abund_quin_panel_filtered <- abund_quin_panel_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  dplyr::rename(year = surv_year) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month))
## combine
abund_quin_panel_select <- abund_quin_panel_filtered %>% 
  left_join(station_covariates_filtered %>% dplyr::select(-county), by = c("cluster_id", "year", "month"))

```

run models
```{r}
### TAR
# build model
mod_fe_abund_pdsi_tar <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_select)

# check summary
summary(mod_fe_abund_pdsi_tar)
confint(mod_fe_abund_pdsi_tar, level = 0.95)
etable(mod_fe_abund_pdsi_tar)


### PIP
# build model
mod_fe_abund_pdsi_pip <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_pip_panel_select)

# check summary
summary(mod_fe_abund_pdsi_pip)
confint(mod_fe_abund_pdsi_pip, level = 0.95)
etable(mod_fe_abund_pdsi_pip)


### QUIN
mod_fe_abund_pdsi_quin <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_quin_panel_select)

# check summary
summary(mod_fe_abund_pdsi_quin)
confint(mod_fe_abund_pdsi_quin, level = 0.95)
etable(mod_fe_abund_pdsi_quin)
```

### WNV MIR
format data
```{r}

## already have
# wnv_tar_panel_under101 


### PIP
## upload culex pipiens data
wnv_pip_panel_full <- read.csv(here("data", "interim", "wnv_pip_cluster.csv"))

wnv_pip_panel_filtered <- wnv_pip_panel_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  dplyr::rename(year = surv_year) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month))

## combine
wnv_pip_panel_select <- wnv_pip_panel_filtered %>% 
  left_join(station_covariates_filtered %>% dplyr::select(-county), by = c("cluster_id", "year", "month"))

wnv_pip_panel_under101 <- wnv_pip_panel_select %>% # 36,478 observations
  filter(WNV_MIR < 101)

### QUINQ
## upload culex quinq data
wnv_quin_panel_full <- read.csv(here("data", "interim", "wnv_quin_cluster.csv"))

wnv_quin_panel_filtered <- wnv_quin_panel_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  dplyr::rename(year = surv_year) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month))
## combine
wnv_quin_panel_select <- wnv_quin_panel_filtered %>% 
  left_join(station_covariates_filtered %>% dplyr::select(-county), by = c("cluster_id", "year", "month"))

wnv_quin_panel_under101 <- wnv_quin_panel_select %>% # 36,478 observations
  filter(WNV_MIR < 101)
```

run models
```{r}
### TAR
# build model
mod_fe_wnv_pdsi_tar <- feols(log(WNV_MIR + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = wnv_tar_panel_under101)

# check summary
summary(mod_fe_wnv_pdsi_tar)
confint(mod_fe_wnv_pdsi_tar, level = 0.95)
etable(mod_fe_wnv_pdsi_tar)


### PIP
# build model
mod_fe_wnv_pdsi_pip <- feols(log(WNV_MIR + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = wnv_pip_panel_under101)

# check summary
summary(mod_fe_wnv_pdsi_pip)
confint(mod_fe_wnv_pdsi_pip, level = 0.95)
etable(mod_fe_wnv_pdsi_pip)


### QUIN
mod_fe_wnv_pdsi_quin <- feols(log(WNV_MIR + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = wnv_quin_panel_under101)

# check summary
summary(mod_fe_wnv_pdsi_quin)
confint(mod_fe_wnv_pdsi_quin, level = 0.95)
etable(mod_fe_wnv_pdsi_quin)
```

## S8.1.2
Spatial units outside alluvial boundary

### Abundance
```{r}
## format data
station_covariates_full2 <- station_covariates_full%>% 
  filter(month %in% 4:10) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month)) 

### TAR
#abund_tar_panel_select

abund_tar_panel_outside <- abund_tar_panel_full %>% 
    filter(county == "Riverside" | county == "Los Angeles" | county == "Orange" | county == "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  dplyr::rename(year = surv_year) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month)) %>% 
  left_join(station_covariates_full2 %>% dplyr::select(-county), by = c("cluster_id", "year", "month"))

#unique(abund_tar_panel_outside$county)

## now just ag based counties
abund_tar_panel_agoutside <- abund_tar_panel_full %>% 
  filter(county == "Riverside" | county == "Shasta") %>% 
    #filter(county != "Los Angeles" | county != "Orange") %>% 
  filter(month %in% 4:10) %>% 
  dplyr::rename(year = surv_year) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month)) %>% 
  left_join(station_covariates_full2 %>% dplyr::select(-county), by = c("cluster_id", "year", "month"))
```

run models
```{r}
### within boundary
# build model
mod_fe_abund_pdsi_tar <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_select)

# check summary
summary(mod_fe_abund_pdsi_tar)
confint(mod_fe_abund_pdsi_tar, level = 0.95)
etable(mod_fe_abund_pdsi_tar)


### outside boundary
### TAR
# build model
mod_fe_abund_pdsi_tar_outside <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_outside)

# check summary
summary(mod_fe_abund_pdsi_tar_outside)
confint(mod_fe_abund_pdsi_tar_outside, level = 0.95)
etable(mod_fe_abund_pdsi_tar_outside)


## ag counties
# build model
mod_fe_abund_pdsi_tar_agoutside <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_agoutside)

# check summary
summary(mod_fe_abund_pdsi_tar_agoutside)
confint(mod_fe_abund_pdsi_tar_agoutside, level = 0.95)
etable(mod_fe_abund_pdsi_tar_agoutside)

```


## S8.2
Measurement uncertainty - need to do this!
```{r}


```
