---
title: "analysis_panelmodels"
output: html_document
---

Manuscript ID: RSTB-2025-0484

Title: Water availability affects West Nile virus dynamics in a heavily managed agricultural landscape

Authors: Samantha Sambado, Andrew J. MacDonald, Alex Konings, and Erin A. Mordecai

Corresponding author: ssambado@stanford.edu

```{r setup, include=FALSE}
## upload necessary packages
library(here)
library(fixest)
library(broom)
```

### upload data
```{r}
## upload culex tarsalis data
abund_tar_panel_full <- read.csv(here("data", "interim", "abundance_tar_cluster.csv"))
wnv_tar_panel_full <- read.csv(here("data", "interim", "wnv_tar_cluster.csv"))

## upload covariate data
station_covariates_full <- read.csv(here("data" ,"interim", "covariates_scalelag_stationmeta.csv"))
```


### filter data for april-october & select counties
```{r}
### ABUNDANCE
abund_tar_panel_filtered <- abund_tar_panel_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  dplyr::rename(year = surv_year) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month))
  
station_covariates_filtered <- station_covariates_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month)) 
## combine
abund_tar_panel_select <- abund_tar_panel_filtered %>% 
  left_join(station_covariates_filtered %>% dplyr::select(-county), by = c("cluster_id", "year", "month"))

#write.csv(abund_tar_panel_select, file = here("data", "derived", "abund_tar_panel_select.csv"), row.names = FALSE)


### WNV MIR
wnv_tar_panel_filtered <- wnv_tar_panel_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  dplyr::rename(year = surv_year) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month))
  
station_covariates_filtered <- station_covariates_full %>% 
  filter(county != "Riverside" & county != "Los Angeles" & county != "Orange" & county != "Shasta") %>% 
  filter(month %in% 4:10) %>% 
  mutate(county = as.factor(county),
         year = as.factor(year),
         month = as.factor(month)) 
## combine
wnv_tar_panel_select <- wnv_tar_panel_filtered %>% 
  left_join(station_covariates_filtered %>% dplyr::select(-county), by = c("cluster_id", "year", "month"))

#write.csv(wnv_tar_panel_select, file = here("data", "derived", "wnv_tar_panel_select.csv"), row.names = FALSE)
```

# Fit models for Main Text 

## Overall Effect of PDSI

### Abundance ~ PDSI
Equation 1
```{r}
# build model
mod_fe_abund_pdsi <- feols(log(mos_per_trap_night + 1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_select)

# check summary
summary(mod_fe_abund_pdsi)
confint(mod_fe_abund_pdsi, level = 0.95)

# look at table
etable(mod_fe_abund_pdsi)

#saveRDS(mod_fe_abund_pdsi,file = here("outputs", "models", "mod_fe_abund_pdsi.rds"))
```

### WNV ~ PDSI
Equation 2
```{r}
# build model - without outliers I can fit 
wnv_tar_panel_under101 <- wnv_tar_panel_select %>% # 36,478 observations
  filter(WNV_MIR < 101) # 36,429 observations

mod_fe_wnv_pdsi <- feols(log(WNV_MIR+1) ~ pdsi_lag0 + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = wnv_tar_panel_under101)

# check summary
summary(mod_fe_wnv_pdsi)
confint(mod_fe_wnv_pdsi, level = 0.95)
# look at table
etable(mod_fe_wnv_pdsi)

#saveRDS(mod_fe_wnv_pdsi,file = here("outputs", "models", "mod_fe_wnv_pdsi.rds"))
```



## Spatial Heterogeneity of PDSI's Effect

### Abundance ~ PDSI*HR
Equation 3
```{r}
# build model
mod_fe_abund_pdsi_HR <- feols(log(mos_per_trap_night + 1) ~ i(hydro_region, pdsi_lag0) + temp_lag0 + I(temp_lag0^2) |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = abund_tar_panel_select)

# check summary
summary(mod_fe_abund_pdsi_HR)
confint(mod_fe_abund_pdsi_HR, level = 0.95)

# look at table
etable(mod_fe_abund_pdsi_HR)

#saveRDS(mod_fe_abund_pdsi_HR,file = here("outputs", "models", "mod_fe_abund_pdsi_HR.rds"))


```


### WNV MIR ~ PDSI*HR
Equation 4
```{r}
# build model
mod_fe_wnv_pdsi_HR <- feols(log(WNV_MIR+ 1) ~ i(hydro_region, pdsi_lag0) + temp_lag0 + I(temp_lag0^2) + bird_lag0 |
                             cluster_id + year + month,
                           vcov = conley(5),
                           data = wnv_tar_panel_under101)

# check summary
summary(mod_fe_wnv_pdsi_HR)
confint(mod_fe_wnv_pdsi_HR, level = 0.95)

# look at table
etable(mod_fe_wnv_pdsi_HR)

#saveRDS(mod_fe_wnv_pdsi_HR,file = here("outputs", "models", "mod_fe_wnv_pdsi_HR.rds"))

```

## Hydrological Variables Associations

(no lags)
### Abundance ~ Hydrological Variables
Equation 5-8
```{r}
## run individual models for each hydrological variable with no time lag
# variables 
hydro_vars <- c("soilmoisture_lag0", "et_lag0", "jrc_5km_lag0", "jrc_10km_lag0")

## make function to build model formula
hydro_formula_abund <- function(var){
  as.formula(paste0("log(mos_per_trap_night + 1) ~ ", var,
                    "+ temp_lag0 + I(temp_lag0^2) | cluster_id + year + month"))
}

## apply function
hydro_mod_abund_nolags <- lapply(hydro_vars, function(v) {
  feols(fml = hydro_formula_abund(v),
        vcov = conley(5),
        data = abund_tar_panel_select)
})


# fix names
names(hydro_mod_abund_nolags) <- hydro_vars

## model summaries
lapply(hydro_mod_abund_nolags, summary)
lapply(hydro_mod_abund_nolags, confint, level = 0.95)

etable(hydro_mod_abund_nolags,
       headers = c("SM", "ET", "SW - 5km", "SW - 10km"),
       dict = c("log(mos_per_trap_night+1" = "Abundance",
                #pdsi = "PDSI",
                temp_lag0 = "Temp (std)",
                temp_lag0 = "Temp^2 (std)"),
       fitstat = ~ n + r2 + wr2,
        digits = 3, style.tex = style.tex("aer"))


#saveRDS(hydro_mod_abund_nolags,file = here("outputs", "models", "mod_fe_abund_hydro_nolags.rds"))
```


### WNV MIR ~ Hydrological Variables
Equation 9-12
```{r}
## run individual models for each hydrological variable with no time lag
# variables 
hydro_vars <- c("soilmoisture_lag0", "et_lag0", "jrc_5km_lag0", "jrc_10km_lag0")

## make function to build model formula
hydro_formula_wnv <- function(var){
  as.formula(paste0("log(WNV_MIR + 1) ~ ", var,
                    "+ temp_lag0 + I(temp_lag0^2) + bird_lag0 | cluster_id + year + month"))
}

## apply function
hydro_mod_wnv_nolags <- lapply(hydro_vars, function(v) {
  feols(fml = hydro_formula_wnv(v),
        vcov = conley(5),
        data = wnv_tar_panel_under101)
})


# fix names
names(hydro_mod_wnv_nolags) <- hydro_vars

## model summaries
lapply(hydro_mod_wnv_nolags, summary)
lapply(hydro_mod_wnv_nolags, confint, level = 0.95)

etable(hydro_mod_wnv_nolags,
       headers = c("SM", "ET", "SW - 5km", "SW - 10km"),
       dict = c("log(WNV_MIR +1)" = "WNV",
                #pdsi = "PDSI",
                temp_lag0 = "Temp (std)",
                temp_lag0 = "Temp^2 (std)",
                bird_lag0 = "Bird (std)"),
       fitstat = ~ n + r2 + wr2,
        digits = 3, style.tex = style.tex("aer"))


#saveRDS(hydro_mod_wnv_nolags,file = here("outputs", "models", "mod_fe_wnv_hydro_nolags.rds"))
```

(with lags)
### Abundance ~ Hydrological Variables
```{r}
## run individual models for each hydrological variable with different time lag
# variables 
hydro_vars_base <- c("soilmoisture", "et", "jrc_5km", "jrc_10km")
lags <- 0:3

# create all variable-lag combos
hydro_vars <- expand.grid(var = hydro_vars_base, lag = lags, stringsAsFactors = FALSE)
hydro_vars$full_var <- paste0(hydro_vars$var, "_lag", hydro_vars$lag)

## make function to build model formula
hydro_formula_abund_lags <- function(var){
  as.formula(paste0("log(mos_per_trap_night + 1) ~ ", var,
                    "+ temp_lag0 + I(temp_lag0^2) | cluster_id + year + month"))
}

## run models
hydro_mod_abund_withlags <- lapply(hydro_vars$full_var,
                                   function(v){feols(fml = hydro_formula_abund_lags(v),
                                           vcov = conley(5),
                                           data = abund_tar_panel_select)
                                   })

names(hydro_mod_abund_withlags) <- hydro_vars$full_var

## model summaries
lapply(hydro_mod_abund_withlags, summary)
lapply(hydro_mod_abund_withlags, confint, level = 0.95)

#saveRDS(hydro_mod_abund_withlags,file = here("outputs", "models", "mod_fe_abund_hydro_withlags.rds"))
```

### WNV MIR ~ Hydrological Variables
```{r}
## run individual models for each hydrological variable with different time lag
# variables 
hydro_vars_base <- c("soilmoisture", "et", "jrc_5km", "jrc_10km")
lags <- 0:3

# create all variable-lag combos
hydro_vars <- expand.grid(var = hydro_vars_base, lag = lags, stringsAsFactors = FALSE)
hydro_vars$full_var <- paste0(hydro_vars$var, "_lag", hydro_vars$lag)

## make function to build model formula
hydro_formula_wnv_lags <- function(var){
  as.formula(paste0("log(WNV_MIR + 1) ~ ", var,
                    "+ temp_lag0 + I(temp_lag0^2) + bird_lag0 | cluster_id + year + month"))
}

## run models
hydro_mod_wnv_withlags <- lapply(hydro_vars$full_var,
                                   function(v){feols(fml = hydro_formula_wnv_lags(v),
                                           vcov = conley(5),
                                           data = wnv_tar_panel_under101)
                                   })

names(hydro_mod_wnv_withlags) <- hydro_vars$full_var

## model summaries
lapply(hydro_mod_wnv_withlags, summary)
lapply(hydro_mod_wnv_withlags, confint, level = 0.95)

#saveRDS(hydro_mod_wnv_withlags,file = here("outputs", "models", "mod_fe_wnv_hydro_withlags.rds"))
```


