---
title: "download_covariates"
output: html_document
---

```{r setup, include=FALSE}
## upload packages
library(here)
library(readr)
library(googledrive)
library(sf)
library(tigris)
library(remotes)
#remotes::install_github("mikejohnson51/climateR")
#library(climateR)
library(stringr)
library(terra)
#remotes::install_git("https://gitlabext.wsl.ch/karger/rchelsa.git")
#library(Rchelsa)
library(purrr)
library(lubridate)
library(tidyr)
library(tidyverse)
library(data.table)

## upload cluster information
#cluster_shp <- st_read(here("data", "spatial_boundaries", "cluster_all_polygon.shp"))
#cluster_info <- read.csv(here("data", "interim", "cluster_all_info.csv"))

## upload california boundaries
options(tigris_use_cache = TRUE)
ca_shp <- tigris::counties("ca", class = "sf")
```

# Covariate 1. PDSI
```{r}
# make AOI
cluster_shp_84 <- st_transform(cluster_shp, 4326)

# pull down data
pdsi_data <- getGridMET(AOI = cluster_shp_84,
                        varname = "pdsi",
                        startDate = "2003-01-01",
                        endDate = "2023-12-31")
# call out pdsi values
pdsi_rast <- pdsi_data$daily_mean_palmer_drought_severity_index

# convert clusters to vect
cluster_vect <- vect(cluster_shp)

# extract average pdsi value within cluster polygon 
pdsi_extract <- terra::extract(pdsi_rast, cluster_vect, fun = mean, weights = TRUE, na.rm = TRUE, bind = TRUE)

# turn into tidy dataframe
pdsi_df <- as.data.frame(pdsi_extract) %>% 
  pivot_longer(cols = starts_with("pdsi_"),
               names_to = "date",
               values_to = "pdsi") %>% 
  mutate(date = as.Date(str_remove(date, "pdsi_"), format = "%Y.%m.%d"),
         year = format(date, "%Y"),
         month = format(date, "%m"))  %>% 
  mutate(year = as.integer(year),
         month = as.integer(month)) %>% 
  dplyr::select(cluster_id, year, month, pdsi) %>% 
  #group_by(cluster_id, year, month) %>% 
  summarise(pdsi = mean(pdsi, na.rm = TRUE), .by = c(cluster_id, year, month))

# save as indiviudal file 
#write.csv(pdsi_df, here("data", "interim", "covariate_pdsi_cluster.csv"))
```


# Covariate 2. Temperature
## Monthly data (2003-2021)
(lives on my google drive)
```{r}
## list chelsa files
chelsa_files <- drive_ls("temperature/CHELSA_tas_ca") %>%
  filter(grepl("\\.tif$", name)) %>%
  mutate(year_month = str_extract(name, "\\d{2}_\\d{4}"),
    month = as.integer(str_extract(year_month, "^\\d{2}")),
    year  = as.integer(str_extract(year_month, "\\d{4}")))

## download once in temp folder
out_dir <- "chelsa_monthly_tmp"
dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)

local_paths <- vector("character", nrow(chelsa_files))

for (i in seq_len(nrow(chelsa_files))) {
  
  f <- chelsa_files[i, ]
  path <- file.path(out_dir, f$name)
  
  if (!file.exists(path)) {
    drive_download(file = f$id,
                   path = path,
                   overwrite = TRUE)
  }
  
  local_paths[i] <- path
}

## stack em
r_stack <- rast(local_paths)

## check the crs
cluster_vect <- vect(st_transform(cluster_shp, crs(r_stack)))

## extract temp means
temp_monthly_vals <- terra::extract(r_stack, cluster_vect, fun = mean, na.rm = TRUE)



## reshape to final df
# correct ID
temp_monthly_vals$cluster_id <- cluster_shp$cluster_id[temp_monthly_vals$ID]
temp_monthly_vals <- temp_monthly_vals[,-1]

# make long
chelsa_cluster_monthly_long <- temp_monthly_vals %>%
  pivot_longer(cols = -cluster_id,
    names_to = "layer",
    values_to = "temp_K") %>%
  mutate(temp_C = temp_K - 273.15) %>%
  dplyr::select(-temp_K)

# create identifiers
meta <- chelsa_files %>%
  mutate(layer = name) %>%
  transmute(layer,year,month)

# clean up
temp_month_df <- chelsa_cluster_monthly_long %>% 
  left_join(meta, by = "layer") %>% 
  mutate(year = substr(layer, 15,18),
         month = substr(layer, 12,13))  %>% 
  mutate(year = as.integer(year),
         month = as.integer(month)) %>% 
  dplyr::select(cluster_id, year, month, temp_C)

#write.csv(temp_month_df, here("data", "interim", "covariate_temp_pre2021_cluster.csv"))
```

## Daily data (2022,2023)
I need to aggregate to monthly but can use the chelsa wrapper
```{r}
## correct spatial extent
ca <- st_transform(ca_shp, 4326)
cluster_vect <- vect(st_transform(cluster_shp, 4326))
ca_extent <- st_bbox(ca)

years <- 2022:2023 # only need data for 2022-2023

results <- list() # store results

for (y in years) {

  for (m in 1:12) {

    month_start <- as.Date(sprintf("%04d-%02d-01", y, m))
    month_end   <- ceiling_date(month_start, "month") - days(1)

    message("processing: ", format(month_start, "%Y-%m"))

    ## download chelsa data
    chelsa_daily <- tryCatch({

      getChelsa(var = "tas",
        extent = c(ca_extent["xmin"],
                   ca_extent["xmax"],
                   ca_extent["ymin"],
                   ca_extent["ymax"]),
        startdate = month_start,
        enddate   = month_end,
        dataset   = "chelsa-daily")

    }, error = function(e) {

      message("failed: ", format(month_start, "%Y-%m"))
      message(e$message)

      return(NULL)
    })

    # skip if nothing downloaded
    if (is.null(chelsa_daily)) next

    ## there are days with missing data so just skip & avg whats there within the month
    n_layers <- nlyr(chelsa_daily)

    if (n_layers == 0) {
      message("no layers found")
      next
    }

    ## create available dates only
    available_dates <- seq.Date(month_start, by = "day", length.out = n_layers)

    names(chelsa_daily) <- as.character(available_dates) # fix names

    ## calc monthly mean
    monthly_raster <- terra::mean(chelsa_daily, na.rm = TRUE)

    names(monthly_raster) <- format(month_start, "%Y-%m")  # fix names

    ## extract cluster mean
    vals <- terra::extract(monthly_raster, cluster_vect, fun = mean, na.rm = TRUE)

    ## convert temp to C
    # CHECK FIRST:
    # plot(monthly_raster)

    mean_val <- global(monthly_raster, mean, na.rm = TRUE)[1,1]

    # if Kelvin convert to C
    if (mean_val > 100) {
      vals[,2] <- vals[,2] - 273.15
    }

    ## store output
    results[[length(results) + 1]] <- data.frame(
      cluster_id = cluster_shp$cluster_id,
      year       = y,
      month      = m,
      year_month = format(month_start, "%Y-%m"),
      temp_C     = vals[,2])

    rm(chelsa_daily, monthly_raster, vals) # remove from comp

    gc()
  }
}

# combine
chelsa_cluster_monthly_2223 <- bind_rows(results)


temp_month_2223_df <- chelsa_cluster_monthly_2223 %>% 
  mutate(year = as.integer(year),
         month = as.integer(month)) %>% 
  dplyr::select(cluster_id, year, month, temp_C)

#write.csv(temp_month_2223_df, here("data", "interim", "covariate_temp_20222023_cluster.csv"))
```

Combine 2003-2021 and 2022-2023 data
```{r}
temp_month_df <- read.csv(here("data", "interim", "covariate_temp_pre2021_cluster.csv")) %>% 
  dplyr::select(-X)

temp_month_both_df <- temp_month_df %>% 
  rbind(temp_month_2223_df, by = c("cluster_id", "year", "month")) %>% 
  mutate(year = as.integer(year),
         month = as.integer(month),
         temp_C = as.numeric(temp_C))

range(temp_month_both_df$year, na.rm = TRUE) # check all year

#write.csv(temp_month_both_df, here("data", "interim", "covariate_temp_both_cluster.csv"), row.names = FALSE)
```

# Covariate 3. Bird Index
(lives on my google drive)
```{r}
drive_auth()
## download rasters from my drive
folder <- drive_get("bird community")

download_bird <- function(file_name, file_id) {
  temp_path <- tempfile(fileext = ".tif")
  
  drive_download(as_id(file_id),
                 path = temp_path,
                 overwrite = TRUE)
  
  r <- terra::rast(temp_path)
  
  message("loaded ", file_name)
  
  return(r)
}

g <- drive_ls(folder) %>% 
  filter(grepl("\\.tif$", name, ignore.case = TRUE))

files <- setNames(g$id, g$name)

# store in list
year_rasters <- lapply(names(files), function(name) {
  download_bird(name, files[[name]])
})

names(year_rasters) <- gsub("\\.tif$", "", names(files))

## convert weekly (52 layers) rasters to monthly (12 layers) values
# assign 4–5 weeks per month
weeks_to_month <- list(month_01 = 1:4,
                       month_02 = 5:8,
                       month_03 = 9:13,
                       month_04 = 14:17,
                       month_05 = 18:21,
                       month_06 = 22:26,
                       month_07 = 27:30,
                       month_08 = 31:35,
                       month_09 = 36:39,
                       month_10 = 40:44,
                       month_11 = 45:48,
                       month_12 = 49:52)

monthly_rasters <- lapply(year_rasters, function(r) {
  monthly <- lapply(names(weeks_to_month), function(month_name) {
    weeks <- weeks_to_month[[month_name]]
    
    terra::mean(r[[weeks]], na.rm = TRUE)
  })
  
  monthly_stack <- terra::rast(monthly)
  names(monthly_stack) <- names(weeks_to_month)
  
  return(monthly_stack)
}) 

## match crs
cluster_vect <- vect(st_transform(cluster_shp, crs(monthly_rasters[[1]])))

## extract monthly means
extract_monthly_bird <- function(monthly_rasters, cluster_vect, cluster_ids) {
  results <- list()
  
  for(year_name in names(monthly_rasters)) {
    r <- monthly_rasters[[year_name]]
    
    ## extract cluster means
    vals <- terra::extract(r, cluster_vect, fun = mean, na.rm = TRUE)
    
    # remove terra ID colum
    vals <- vals[,-1]
    
    # add cluster_id
    vals$cluster_id <- cluster_ids
    
    ## turn into long df
    vals_long <- vals %>% 
      tidyr::pivot_longer(cols = starts_with("month_"),
                   names_to = "month",
                   values_to = "bird_comp") %>% 
      mutate(year = year_name,
             month = as.integer(gsub("month_", "", month))) %>% 
      dplyr::select(cluster_id, year, month, bird_comp)
    
    results[[year_name]] <- vals_long
  }
  
  dplyr::bind_rows(results)
}

## run extraction
bird_cluster <- extract_monthly_bird(monthly_rasters = monthly_rasters,
                                     cluster_vect = cluster_vect,
                                     cluster_ids = cluster_shp$cluster_id)

bird_cluster_df <- bird_cluster %>% 
  mutate(year = substr(year, nchar(year)-3, nchar(year)))  %>% 
  mutate(year = as.integer(year),
         month = as.integer(month)) %>% 
  dplyr::select(cluster_id, year, month, bird_comp)

#write.csv(bird_cluster_df, here("data", "interim", "covariate_bird_cluster.csv"), row.names = FALSE)
```

# Covariate 4. Soil Moisture from CCI
(pre-processed monthly averages in Google Earth Engine and stored in my google drive)
```{r}
## authenticate, connect Gdrive
drive_auth()
folder <- drive_get("CCI_soilmoisture/2003_2023")
g <- drive_ls(folder) %>% dplyr::filter(grepl("\\.nc$", name))
files <- setNames(g$id, g$name)

## download & stack soil moisture files
read_nc <- function(file_id, file_name) {
  tmp <- tempfile(fileext = ".nc")
  drive_download(as_id(file_id), path = tmp, overwrite = TRUE)
  rast(tmp, subds = "sm")
}

r_list <- lapply(names(files), function(nm) {
  read_nc(files[[nm]], nm)
})

r <- do.call(c, r_list)

## fix dates from file name
dates <- as.Date(str_extract(names(files), "\\d{8}"),"%Y%m%d")

names(r) <- format(dates, "%Y_%m")
time(r) <- dates

## correct crs
clusters_vect <- vect(st_transform(cluster_shp, crs(r)))

## extract mean SM for each cluster
vals <- terra::extract(r, clusters_vect, fun = mean, na.rm = TRUE)

## convert to long dataframe
vals <- as.data.frame(vals)
vals <- vals[,-1]
vals$cluster_id <- cluster_shp$cluster_id

# tidy up
soil_cluster_monthly <- vals %>%
  tidyr::pivot_longer(cols = -cluster_id,
               names_to = "year_month",
               values_to = "soil_moisture") %>%
  mutate(date = as.Date(paste0(gsub("_", "-", year_month), "-01")),
    year = format(date, "%Y"),
    month = format(date, "%m")) %>%
  group_by(cluster_id, year, month) %>%
  dplyr::summarise(soilmoisture = mean(soil_moisture, na.rm = TRUE),.groups = "drop")



soil_cluster_df <- soil_cluster_monthly %>% 
  mutate(year = as.integer(year),
         month = as.integer(month)) %>% 
  dplyr::select(cluster_id, year, month, soilmoisture)

#write.csv(soil_cluster_df, here("data", "interim", "covariate_soilmoisture_cluster.csv"), row.names = FALSE)
```

## Covariate 5. ET from GLEAM
(processed on GEE and stored in my google folder)
```{r}
## authenticate, connect Gdrive
drive_auth()

folder <- drive_get("hydrology/GLEAM_et")
g <- drive_ls(folder) %>% dplyr::filter(grepl("\\.nc$", name)) %>% arrange(name)
files <- setNames(g$id, g$name)

## download and stack
r_list <- lapply(names(files), function(nm) {
  tmp <- tempfile(fileext = ".nc")
  drive_download(as_id(files[[nm]]), path = tmp, overwrite = TRUE)
  rast(tmp)
})

r_stack <- do.call(c, r_list)

## fix dates based on file name
names(r_stack) <- format(time(r_stack), "%Y_%m")

## correct crs of clusters
clusters_vect <- vect(st_transform(cluster_shp, 4326))

## crop
ca_extent <- ext(-124, -113, 32, 42)
r_stack <- crop(r_stack, ca_extent)

## extract ET means to clusters
vals <- terra::extract(r_stack, clusters_vect, fun = mean, na.rm = TRUE)

## make long dataframe
vals <- as.data.frame(vals)
vals <- vals[,-1]
vals$cluster_id <- cluster_shp$cluster_id

# tidy it up
gleam_et_monthly <- vals %>%
  tidyr::pivot_longer(cols = -cluster_id,
                      names_to = "year_month",
                      values_to = "ET_mm") %>%
  mutate(date = as.Date(paste0(gsub("_", "-", year_month), "-01")),
    year = format(date, "%Y"),
    month = format(date, "%m")) %>%
  dplyr::select(cluster_id, year, month, ET_mm) 

et_cluster_df <- gleam_et_monthly %>% 
  mutate(year = as.integer(year),
         month = as.integer(month)) %>% 
  dplyr::select(cluster_id, year, month, ET_mm)

#write.csv(et_cluster_df, here("data", "interim", "covariate_et_cluster.csv"), row.names = FALSE)
```

## Covariate 6. Standing Surface Water from JRC
(processed on GEE and stored in my google folder)

#### within 5 km buffers
```{r}
years <- 2003:2021

water_dt <- map_dfr(years, \(y){
  file <- here("data", "raw","public", "jrc_pct_5km",
               glue::glue("JRC_water_pct_traps_5km_{y}.csv"))
  
  read_csv(file, col_select = c(cluster_id,year, month, water_pct), show_col_types = FALSE)
})

jrc_5km_cluster_df <- water_dt %>% 
  mutate(year = as.integer(year),
         month = as.integer(month),
         jrc_5km = water_pct) %>% 
  dplyr::select(cluster_id, year, month, jrc_5km)

#write.csv(jrc_5km_cluster_df, here("data", "interim", "covariate_jrc5km_cluster.csv"), row.names = FALSE)

```



#### within 10 km buffers
```{r}
years <- 2003:2021

water_dt <- map_dfr(years, \(y){
  file <- here("data", "raw","public", "jrc_pct_10km",
               glue::glue("JRC_water_pct_traps_10km_{y}.csv"))
  
  read_csv(file, col_select = c(cluster_id,year, month, water_pct), show_col_types = FALSE)
})

jrc_10km_cluster_df <- water_dt %>% 
  mutate(year = as.integer(year),
         month = as.integer(month),
         jrc_10km = water_pct) %>% 
  dplyr::select(cluster_id, year, month, jrc_10km)

#write.csv(jrc_10km_cluster_df, here("data", "interim", "covariate_jrc10km_cluster.csv"), row.names = FALSE)

```

## Covariates for Figure 1

Need to create shp file for GEE to pull down hydrological regions data but make sure it's only for data within alluvial boundary 
```{r}
# upload and transform crs
HR <- st_read(here("data", "spatial_boundaries", "i03_Hydrologic_Regions", "i03_Hydrologic_Regions.shp")) 

cv <- st_read(here("data", "spatial_boundaries", "centralvalley", "centralvalley.shp")) %>% 
  st_transform(st_crs(HR))

# filter for 3 regions
HR_filtered <- HR %>% 
  filter(HR_NAME %in% c("Sacramento River", "San Joaquin River", "Tulare Lake"))

# clip regions to alluvial boundary
HR_cv <- HR_filtered %>% 
  st_intersection(cv)

#plot(HR_cv) # check

# save as a shp file for GEE
#st_write(HR_cv, here("data", "spatial_boundaries", "HR_cv", "HR_cv.shp"), delete_layer = TRUE)
```


