---
title: "create_paneldata"
output: html_document
---

```{r setup, include=FALSE}
library(sf)
library(here)

stations_all <- read.csv(here("data", "interim", "cluster_all_info.csv")) %>% 
  dplyr::select(-X)
```

# Create outcomes 

## Abundance

### Make function to create mos per trap night per speces
```{r}
abundace_panel_species <- function(data, species_name){
  data %>% 
    filter(species == species_name) %>% 
    group_by(county, cluster_id, surv_year, month) %>% 
    summarise(n_traps = n_distinct(trapstation_id),
      total_mos = sum(num_clean, na.rm = TRUE),
      total_trap_nights = sum(trap_nights, na.rm = TRUE),
      mos_per_trap_night = total_mos / total_trap_nights,
      .groups = "drop") %>% 
    arrange(county, cluster_id, surv_year, month)
}

```

### Apply function to make individual datasets
```{r}
abund_tar_panel <- abundace_panel_species(abundance_all_clustered, "Cx tarsalis")
abund_pip_panel <- abundace_panel_species(abundance_all_clustered, "Cx pipiens")
abund_quin_panel <- abundace_panel_species(abundance_all_clustered, "Cx quinquefasciatus")

```

### Save files
```{r}
write_csv(abund_tar_panel, here("data", "interim", "abundance_tar_cluster.csv"))
write_csv(abund_pip_panel, here("data", "interim", "abundance_pip_cluster.csv"))
write_csv(abund_quin_panel, here("data", "interim", "abundance_quin_cluster.csv"))

```

## WNV MIR

### Make function to create WNV MIR per speces
```{r}
wnv_panel_species <- function(data, species_name){
  data %>% 
    filter(species == species_name) %>% 
    group_by(county, cluster_id, surv_year, month) %>% 
    summarise(n_traps = n_distinct(trapstation_id),
              total_pools = n(),
              positive_pools = sum(test_status == "Confirmed", na.rm = TRUE),
              total_mos_tested = sum(num_clean, na.rm = TRUE),
              WNV_MIR = ifelse(total_mos_tested > 0,
                               (positive_pools / total_mos_tested)*1000, NA_real_), .groups = "drop") %>% 
    arrange(county, cluster_id, surv_year, month)
}

```

### Apply function to make individual datasets
```{r}
wnv_tar_panel <- wnv_panel_species(wnv_all_clustered, "Cx tarsalis")
wnv_pip_panel <- wnv_panel_species(wnv_all_clustered, "Cx pipiens")
wnv_quin_panel <- wnv_panel_species(wnv_all_clustered, "Cx quinquefasciatus")
```
### Save files
```{r}
write_csv(wnv_tar_panel, here("data", "interim", "wnv_tar_cluster.csv"))
write_csv(wnv_pip_panel, here("data", "interim", "wnv_pip_cluster.csv"))
write_csv(wnv_quin_panel, here("data", "interim", "wnv_quin_cluster.csv"))

```

# Create covariate data to merge onto outcomes

### slim down station info 
```{r}
## slim station info
stations_all_slim <- stations_all %>% 
  distinct(cluster_id, .keep_all = TRUE) %>% 
  dplyr::select(-trapstation_id)
```

### add hydrological region
```{r}
counties_sac <- c("Butte", "Glenn", "Colusa", "Yolo", "Sacramento",
                  "Placer", "Yuba", "Shasta", "Tehama", "Sutter", "Shasta")

counties_sanjoaquin <- c("San Joaquin", "Stanislaus", "Merced","Madera", "Fresno")

counties_tulare <- c("Kings", "Tulare", "Kern")

county_to_hr <- dplyr::bind_rows(data.frame(county = counties_sac, hydro_region = "Sacramento River HR"),
  data.frame(county = counties_sanjoaquin,hydro_region = "San Joaquin River HR"),
  data.frame(county = counties_tulare,hydro_region = "Tulare Lake HR"))

```

### add meta data and covariates to station info
```{r}
covariates_full <- read.csv(here("data", "interim","covariates_combined_scalelag.csv"))

station_covariates_full <- stations_all_slim %>% 
  left_join(county_to_hr, by = "county") %>% 
  left_join(covariates_full, by = "cluster_id")

write.csv(station_covariates_full, file = here("data" ,"interim", "covariates_scalelag_stationmeta.csv"), row.names = FALSE)
```

